### 2016-06-24 SIG Proceedings Template-Jan2015 Zip/paper.tex
add experiments results && paper script

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{A Failure Detection Model in Data Center Network\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kai Shen\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \email{knshen@sjtu.edu.cn}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{Failure Detection; Data Center Networks}

\section{Introduction}

\section{Related Works}

\section{Data Center Background}

\section{Failure Detection Model}

\section{Evaluation}

\section{Conclusion and Future Works}

\section{Acknowledgement}

\section{References}

\end{document}

### 2016-06-24 SIG Proceedings Template-Jan2015 Zip/sig-alternate-sample.tex
add experiments results && paper script

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{A Failure Detection Model in Data Center Network\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{8} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kai Shen\titlenote{Dr.~Trovato insisted his name be first.}\\
       \affaddr{School of Software}\\
       \affaddr{Shanghai Jiao Tong University}\\
       \affaddr{Wallamaloo, New Zealand}\\
       \email{knshen@sjtu.edu.cn}
% 2nd. author
\alignauthor
G.K.M. Tobin\titlenote{The secretary disavows
any knowledge of this author's actions.}\\
       \affaddr{Institute for Clarity in Documentation}\\
       \affaddr{P.O. Box 1212}\\
       \affaddr{Dublin, Ohio 43017-6221}\\
       \email{webmaster@marysville-ohio.com}
% 3rd. author
\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
one who did all the really hard work.}\\
       \affaddr{The Th{\o}rv{\"a}ld Group}\\
       \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
       \affaddr{Hekla, Iceland}\\
       \email{larst@affiliation.org}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor Lawrence P. Leipuner\\
       \affaddr{Brookhaven Laboratories}\\
       \affaddr{Brookhaven National Lab}\\
       \affaddr{P.O. Box 5000}\\
       \email{lleipuner@researchlabs.org}
% 5th. author
\alignauthor Sean Fogarty\\
       \affaddr{NASA Ames Research Center}\\
       \affaddr{Moffett Field}\\
       \affaddr{California 94035}\\
       \email{fogartys@amesres.org}
% 6th. author
\alignauthor Charles Palmer\\
       \affaddr{Palmer Research Laboratories}\\
       \affaddr{8600 Datapoint Drive}\\
       \affaddr{San Antonio, Texas 78229}\\
       \email{cpalmer@prl.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ACM proceedings; \LaTeX; text tagging}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps} files to be
displayable with \LaTeX.  If you work with pdf\LaTeX, use files in the
\textbf{.pdf} format.  Note that most modern \TeX\ system will convert
\textbf{.eps} to \textbf{.pdf} for you on the fly.  More details on
each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{fly}
\caption{A sample black and white graphic
that has been resized with the \texttt{includegraphics} command.}
\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

\begin{figure*}
\centering
\includegraphics{flies}
\caption{A sample black and white graphic
that needs to span two columns of text.}
\end{figure*}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{rosette}
\caption{A sample black and white graphic that has
been resized with the \texttt{includegraphics} command.}
\vskip -6pt
\end{figure}

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

### 2016-06-24 src/relatedWork/kdd2014/AzureLocator.java

@@ -202,8 +202,12 @@ public class AzureLocator {
 
 	}
 
+	public void run() throws IOException {
+		
+	}
+	
 	public static void main(String[] args) throws IOException {
-		AzureLocator al = new AzureLocator("z://ping1//");
+		AzureLocator al = new AzureLocator("z://linkCrashDump//ping-2-1//");
 		al.getAllPath(); //get all possible shortest paths from i to j
 		al.computeEdgeAndVertexPro(); // compute pro_i_i_e && pro_i_j_v
 		
@@ -218,11 +222,12 @@ public class AzureLocator {
 			System.out.println(edge + ": " + link_failure.get(i));
 		}
 		
+		/*
 		System.out.println("------------------------------");
 		
 		for(int i=0; i<device_failure.size(); i++) {
 			System.out.println("node " + i + ": " + device_failure.get(i));
-		}
+		} */
 		System.out.println();
 
 	}

### 2016-06-25 SIG Proceedings Template-Jan2015 Zip/paper.tex
update paper

@@
 
-\title{A Failure Detection Model in Data Center Network\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
-\subtitle{[Extended Abstract]
-\titlenote{A full version of this paper is available as
-\textit{Author's Guide to Preparing ACM SIG Proceedings Using
-\LaTeX$2_\epsilon$\ and BibTeX} at
-\texttt{www.acm.org/eaddress.htm}}}
+\title{A Failure Detection Model in Data Center Network}
+
 %
@@
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
 

### 2016-06-25 SIG Proceedings Template-Jan2015 Zip/paper.tex
write paper

@@
 
-\title{A Failure Detection Model in Data Center Network}
-
+\title{A Failure Detection Model for Data Center Networks\titlenote{(Produces the permission block, and
+copyright information). For use with
+SIG-ALTERNATE.CLS. Supported by ACM.}}
 %
@@
        \affaddr{Shanghai Jiao Tong University}\\
+       \affaddr{Wallamaloo, New Zealand}\\
        \email{knshen@sjtu.edu.cn}
 % 2nd. author
-\alignauthor
-G.K.M. Tobin\titlenote{The secretary disavows
-any knowledge of this author's actions.}\\
-       \affaddr{Institute for Clarity in Documentation}\\
-       \affaddr{P.O. Box 1212}\\
-       \affaddr{Dublin, Ohio 43017-6221}\\
-       \email{webmaster@marysville-ohio.com}
+\alignauthor Charles Palmer\\
+       \affaddr{Palmer Research Laboratories}\\
+       \affaddr{8600 Datapoint Drive}\\
+       \affaddr{San Antonio, Texas 78229}\\
+       \email{cpalmer@prl.com}
 }
+% There's nothing stopping you putting the seventh, eighth, etc.
+% author on the opening page (as the 'third row') but we ask,
+% for aesthetic reasons that you place these 'additional authors'
+% in the \additional authors block, viz.
+% Just remember to make sure that the TOTAL number of authors
+% is the number that will appear on the first page PLUS the
+% number that will appear in the \additionalauthors section.
 
@@
 
-\keywords{Failure Detection; Data Center Networks}
+\keywords{ACM proceedings; \LaTeX; text tagging}
 
 \section{Introduction}
+Data center.
+The rest of this paper is organized as follows. Section 2 discusses related work,
 
-\section{Related Works}
+\section{Related Work}
+In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure localization in data center networks.
 
-\section{Data Center Background}
+\subsection{Failure Detectors}
+A failure detector(FD) is widely recognized as an oracle to intelligently suspect failed processes \cite{chandra1996unreliable}.
+The monitored process periodically send heartbeat messages to its detector to prove its liveness.
 
-\section{Failure Detection Model}
+Chen et al.
+proposed a FD that provides QoS \cite{chen2002quality}.
+It estimates the expected arrival time(EAs) of the next heartbeat message according to a slide window storing n most recent arrived messages.
+EAs determine the deadline that the detector will wait for the next heartbeat before suspecting the monitored process.
+\textit{Chen FD} can adjust current network condition and set the timeout threshold adaptively by referring to recent heartbeats.
+Bertier et al.
+proposed a similar FD \cite{bertier2002implementation}, whereas it uses a dynamic way to compute error margin of \textit{Chen FD}.
+Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output an accrual failure value at any time which stands for the failure probability of the process.
 
+\subsection{Failure Detection Architecture}
+A failure detection architecture aims to provide the service of monitoring nodes in large scale distributed systems in a scalable way.
+Roughly speaking, there are two kinds of architectures.
+The first one is hierarchical architecture \cite{felber1999failure}, all the nodes are partitioned into different groups, each group has a leader node.
+Within a group, the leader node is responsible for monitoring all the nodes.
+Leader nodes periodically send node status information of his group to other leader nodes.
+Hierarchical architecture can reduce the number of heartbeat messages effectively, but it exists \textit{Single Point of Failure} problem, when the leader node crashes, it needs to select a new leader.
+Another alternative solution is Gossip-Style architecture \cite{van1998gossip}.
+Each node maintains a list containing the \textit{heartbeat counter} for all the nodes in the system.
+Every T$_{gossip}$ seconds, each node firstly update \textit{heartbeat counter} of itself and then randomly select another node to send its list to.
+Upon receiving a message, the node will merge two lists and update each node's \textit{heartbeat counter} with the bigger one.
+If the \textit{heartbeat counter} does not update after T$_{fail}$ seconds, the node will be marked as crashed.
+If the \textit{heartbeat counter} does not update after T$_{cleanup}$(T$_{cleanup}$
+$\ge$T$_{fail}$) seconds, it will be removed from the list.
 \section{Evaluation}
 
-\section{Conclusion and Future Works}
+\section{Conclusions}
+This paper proposes a failure detector model for data center networks.
+%\end{document}  % This is where a 'short' article might terminate
 
-\section{Acknowledgement}
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
+This work is partially supported by the National High-Technology Research and Development Program of China under Grant No.2014AA01A301.
 
-\section{References}
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
 

### 2016-06-25 src/core/LinkFailureDetector.java

@@ -3,15 +3,17 @@ package core;
 import java.util.*;
 import java.io.*;
 
+import evaluation.Evaluator;
 import ml.ArffMaker;
 import ml.ClassifyModeller;
 import parser.DumpAnalyzer;
+import util.Item;
 import util.Route;
 import util.Util;
 
 public class LinkFailureDetector {
 	// parameters
-	public static final int check_interval = 2;
+	public static final int check_interval = 1;
 	
 	public static final List<String> directions = new ArrayList<String>();
 	public List<String> class_values = new ArrayList<String>();
@@ -24,19 +26,23 @@ public class LinkFailureDetector {
 				directions.add(i + "-->" + j);
 	}
 	
-	public void dataConstructor() throws IOException {	
+	public void dataConstructor(String dump_dir, String mark, boolean isTrain) throws IOException {	
 		DumpAnalyzer da = null;
-		File dir = new File("z://");
+		File dir = new File(dump_dir);
 		class_values.add("normal");
 		for(File file : dir.listFiles()) {
-			if(file.isDirectory() && file.getName().startsWith("link")) {
+			if(file.isDirectory() && file.getName().startsWith(mark)) {
 				//System.out.println("# " + file.getName());
 				
 				da = new DumpAnalyzer(file.getAbsolutePath());
 				List<List<Map<String, Integer>>> res = da.getRSPackets(check_interval, 59);
 				
 				// form instances	
-				String class_value = file.getName().replaceAll(" ", "");
+				String class_value = "";
+				if(isTrain)
+					class_value = file.getName().replaceAll(" ", "");
+				else
+					class_value = "normal";
 				
 				if(!class_value.endsWith("test")) {
 					class_values.add(class_value);
@@ -64,14 +70,33 @@ public class LinkFailureDetector {
 				}
 			}
 		}
-		System.out.println();
+		//System.out.println();
 	}
 
-	public void detect() throws IOException {
+	public void detect(String train_dump_dir, String test_dump_dir, String mark) throws Exception {	
+		// load train data
+		//dataConstructor(train_dump_dir, "link", true);	
+		// ArffMaker.make("train.arff", instances, classes, class_values); 
+		// load test data
+		dataConstructor(test_dump_dir, mark, false);
+		ArffMaker.make("test.arff", instances, classes, class_values); 
+		
[…]

### 2016-06-25 src/evaluation/Evaluator.java

@@ -2,6 +2,7 @@ package evaluation;
 
 import java.util.*;
 
+import util.Item;
 import util.TimePeriod;
 
 public class Evaluator {
@@ -95,8 +96,39 @@ public class Evaluator {
 		return false;
 	}
 	
-	public static void main(String[] args) {
-
+	/**
+	 * smaller, better
+	 * @param suspects
+	 * @param size
+	 * @return
+	 */
+	public static double discrimination(List<Item> suspects) {
+		//final int num_states = suspects.size() - 1;
+		double pro4Links = 0;
+		for(int i=0; i<suspects.size(); i++) {
+			if(!suspects.get(i).item_name.equals("normal"))
+				pro4Links += suspects.get(i).value;
+		}
+		
+		double res = 0;
+		for(int i=0; i<suspects.size(); i++) {
+			if(suspects.get(i).item_name.equals("normal"))
+				continue;
+			double pro = suspects.get(i).value / pro4Links;
+			res += pro * ((Math.log(pro)) / (Math.log(2)));		
+		}
+		return res * -1;
 	}
+	
+	public static void main(String[] args) {
+		List<Item> sus = new ArrayList<Item>();
+		sus.add(new Item("aa", 0.96));
+		sus.add(new Item("aa", 0.01));
+		sus.add(new Item("aa", 0.01));
+		sus.add(new Item("aa", 0.01));
+		sus.add(new Item("aa", 0.01));
+		
+		System.out.println(Evaluator.discrimination(sus));
+	} 
 
 }

### 2016-06-25 src/ml/ArffMaker.java

@@ -16,13 +16,9 @@ public class ArffMaker {
 		for (int i = 0; i < num_attr; i++) {
 			bw.write("@ATTRIBUTE attr" + i + " NUMERIC\n");
 		}
-		String str = "";
-		for (int i = 0; i < class_values.size() - 1; i++) {
-			str += class_values.get(i) + ",";
-		}
-		str += class_values.get(class_values.size() - 1);
+		String str = "@ATTRIBUTE class {normal,link0-2,link0-3,link0-4,link0-5,link1-2,link1-3,link1-4,link1-5,link2-6,link2-7,link2-8,link3-6,link3-7,link3-8,link4-10,link4-11,link4-9,link5-10,link5-11,link5-9}";
 
-		bw.write("@ATTRIBUTE class {" + str + "}\n");
+		bw.write(str + "\n");
 		bw.write("@DATA\n");
 
 		int pos = 0;
@@ -55,7 +51,7 @@ public class ArffMaker {
 		int train_size = (int) (data.size() * factor);
 		int test_size = data.size() - train_size;
 
-		if(isShuffle) {
+		if (isShuffle) {
 			// shuffle
 			for (int k = 0; k < 10000; k++) {
 				int i = (int) (Math.random() * data.size());
@@ -64,7 +60,7 @@ public class ArffMaker {
 				Collections.swap(classes, i, j);
 			}
 		}
-	
+
 		List<List<Integer>> train_data = new ArrayList<List<Integer>>();
 		List<String> train_classes = new ArrayList<String>();
 		List<List<Integer>> test_data = new ArrayList<List<Integer>>();

### 2016-06-25 src/ml/ClassifyModeller.java

@@ -3,11 +3,13 @@ package ml;
 import java.util.*;
 import java.io.*;
 
+import util.Item;
 import weka.classifiers.Classifier;
 import weka.classifiers.bayes.BayesNet;
 import weka.classifiers.functions.MultilayerPerceptron;
 import weka.classifiers.trees.J48;
 import weka.core.Instances;
+import weka.core.SerializationHelper;
 import weka.core.converters.ArffLoader;
 
 public class ClassifyModeller {
@@ -23,7 +25,7 @@ public class ClassifyModeller {
 				"link5-10", "link5-11", "link5-9");
 	}
 
-	public void load() throws IOException {
+	private void load() throws IOException {
 		File file = new File("train.arff");
 		ArffLoader atf = new ArffLoader();
 		atf.setFile(file);
@@ -33,35 +35,41 @@ public class ClassifyModeller {
 		ins_test = atf.getDataSet();
 	}
 
-	public void classify() throws Exception {
+	public List<List<Item>> classify() throws Exception {
+		List<List<Item>> ress = new ArrayList<List<Item>>();
 		load();
 		ins_train.setClassIndex(216);
 		ins_test.setClassIndex(216);
 
-		Classifier cr = new MultilayerPerceptron();
-		cr.buildClassifier(ins_train);
-
-		int correct = 0;
+		File model = new File("ann.model");
+		
+		// Serialize
+		if(!model.exists()) {
+			Classifier cr = new MultilayerPerceptron();
+			cr.buildClassifier(ins_train);
+			SerializationHelper.write("ann.model", cr);
+		}
+			
+		Classifier cr = (Classifier)SerializationHelper.read("ann.model");
+				
 		for (int i = 0; i < ins_test.numInstances(); i++) {
+			// one instance:
+			List<Item> list = new ArrayList<Item>();
+			
 			double res = cr.classifyInstance(ins_test.instance(i));
-			double should = ins_test.instance(i).classValue();
+			//double should = ins_test.instance(i).classValue();
 			double pro[] = cr.distributionForInstance(ins_test.instance(i));
 
 			for(int j=0; j<pro.length; j++) {
-				System.out.print(class_mapping.get(j) + ": " + pro[j] + "	");
+				list.add(new Item(class_mapping.get(j), pro[j]));
+				//System.out.print(class_mapping.get(j) + ": " + pro[j] + "	");
 			}
 			
-			System.out.println();
-			/*
-			if (res == should) {
[…]

### 2016-06-25 src/relatedWork/kdd2014/AzureLocator.java

@@ -4,6 +4,7 @@ import java.util.*;
 import java.io.*;
 
 import util.BiTreeNode;
+import util.Item;
 import util.Route;
 import util.Node;
 import util.Util;
@@ -18,9 +19,9 @@ class Edge {
 	}
 
 	public String toString() {
-		return v1 + " -- " + v2;
+		return v1 + "-" + v2;
 	}
-	
+
 	public boolean equals(Object obj) {
 		Edge other = (Edge) obj;
 		return (v1 == other.v1 && v2 == other.v2)
@@ -41,7 +42,7 @@ public class AzureLocator {
 	public Map<Route, BiTreeNode> paths = new HashMap<Route, BiTreeNode>();
 	public double pro_i_j_e[][][];
 	public double pro_i_j_v[][][];
-	
+
 	public AzureLocator(String dir) throws IOException {
 		pp = new PingParser(dir);
 		dis = new int[pp.num_nodes][pp.num_nodes];
@@ -59,7 +60,7 @@ public class AzureLocator {
 				}
 			}
 		}
-		
+
 		pro_i_j_e = new double[pp.num_nodes][pp.num_nodes][edges.size()];
 		pro_i_j_v = new double[pp.num_nodes][pp.num_nodes][pp.num_nodes];
 		pp.getPingData();
@@ -67,56 +68,60 @@ public class AzureLocator {
 
 	/**
 	 * locate device failure
+	 * 
 	 * @return
 	 */
 	public List<Double> locateDeviceFailure() {
 		List<Double> v_e = new ArrayList<Double>();
-		
-		for(int device_id=0; device_id<pp.num_nodes; device_id++) {
-			double numerator = 0; 
+
+		for (int device_id = 0; device_id < pp.num_nodes; device_id++) {
+			double numerator = 0;
 			double denominator = 0;
-			
-			for(int i=0; i<pp.num_nodes; i++) {
-				for(int j=0; j<pp.num_nodes; j++) {
+
+			for (int i = 0; i < pp.num_nodes; i++) {
+				for (int j = 0; j < pp.num_nodes; j++) {
 					// i ----ping----> j
-					if(i == j)
+					if (i == j)
 						continue;
 					double pr = pro_i_j_v[i][j][device_id];
-					numerator += (pp.total_pings.get(i).get(j) - pp.success_pings.get(i).get(j)) * pr;
+					numerator += (pp.total_pings.get(i).get(j) - pp.success_pings
[…]

### 2016-06-25 src/util/Item.java

@@ -1,0 +1,22 @@
+package util;
+
+public class Item implements Comparable {
+	public String item_name;
+	public double value;
+	
+	public Item(String in, double v) {
+		this.item_name = in;
+		this.value = v;
+	}
+	
+	@Override
+	public int compareTo(Object o) {
+		Item item = (Item) o;
+		if(value > item.value)
+			return -1;
+		else if(value == item.value)
+			return 0;
+		return 1;
+	}
+	
+}

### 2016-06-25 src/util/Util.java

@@ -9,6 +9,22 @@ import java.util.*;
 
 public class Util {
 	
+	public static double residual(List<Item> list1, List<Item> list2) {
+		double res = 0;
+		for(Item i1 : list1) {
+			Item other = null;
+			for(int i=0; i<list2.size(); i++) {
+				Item i2 = list2.get(i);
+				if(i2.item_name.equals(i1.item_name)) {
+					other = i2;
+					break;
+				}	
+			}
+			res += (i1.value - other.value) * (i1.value - other.value);
+		}
+		return res;
+	}
+	
 	public static int C_N_M(int n, int m) {
 		return factorial(n) / (factorial(m) * factorial(n - m));
 	}

### 2016-06-26 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing paper

@@
 
-\title{A Failure Detection Model for Data Center Networks\titlenote{(Produces the permission block, and
+\title{A Failure Detection approach of Data Center Networks\titlenote{(Produces the permission block, and
 copyright information). For use with
@@
 \section{Related Work}
-In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure localization in data center networks.
+In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure detection in data center networks.
 
 \subsection{Failure Detectors}
-A failure detector(FD) is widely recognized as an oracle to intelligently suspect failed processes \cite{chandra1996unreliable}.
+A failure detector (FD) is widely recognized as an oracle to intelligently suspect failed processes \cite{chandra1996unreliable}.
 The monitored process periodically send heartbeat messages to its detector to prove its liveness.
@@
 proposed a FD that provides QoS \cite{chen2002quality}.
-It estimates the expected arrival time(EAs) of the next heartbeat message according to a slide window storing n most recent arrived messages.
+It estimates the expected arrival time (EAs) of the next heartbeat message according to a slide window storing n most recent arrived messages.
 EAs determine the deadline that the detector will wait for the next heartbeat before suspecting the monitored process.
@@
 proposed a similar FD \cite{bertier2002implementation}, whereas it uses a dynamic way to compute error margin of \textit{Chen FD}.
-Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output an accrual failure value at any time which stands for the failure probability of the process.
+Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output a continuous accrual failure value other than a binary value at any time which stands for the failure probability of the process.
 
@@
 Hierarchical architecture can reduce the number of heartbeat messages effectively, but it exists \textit{Single Point of Failure} problem, when the leader node crashes, it needs to select a new leader.
+
 Another alternative solution is Gossip-Style architecture \cite{van1998gossip}.
-Each node maintains a list containing the \textit{heartbeat counter} for all the nodes in the system.
+Each node maintains a list containing the \textit{heartbeat counter} for each node in the system.
 Every T$_{gossip}$ seconds, each node firstly update \textit{heartbeat counter} of itself and then randomly select another node to send its list to.
@@
 If the \textit{heartbeat counter} does not update after T$_{fail}$ seconds, the node will be marked as crashed.
-If the \textit{heartbeat counter} does not update after T$_{cleanup}$(T$_{cleanup}$
+If the \textit{heartbeat counter} does not update after T$_{cleanup}$ (T$_{cleanup}$
 $\ge$T$_{fail}$) seconds, it will be removed from the list.
+This approach has very low bandwidth occupation because it only produces $n$ messages each epoch where $n$ is the size of the system.
+However, with the increasing of crashing nodes, it needs more time to detect these failures.
+
+\subsection{Failure Detection in Networks}
+Different from the work mentioned above, failure detection in networks should consider network topology and localize failure positions at IP layer.
+Gill et al.
+present the first large-scale survey on failures in data center networks \cite{gill2011understanding}.
+
+Also, there exists a large body of work on applying statistical approaches to failure localization in networks.
+Sherlock \cite{bahl2007towards} localizes failures to limited network components by capturing dependencies between components.
+Shrink \cite{kandula2005shrink} leverages Bayesian Network model to diagnose root cause of IP network failures.
+Herodotou et al.
+\cite{herodotou2014scalable} actively inject ping traffic into network and analyze the ping results overlaid on top of the network topology.
+It will generate a ranked list containing the suspected failed device and links along with their failure score that can best explain the observed ping data.
+
+\section{Data Center Network Architecture}
+In this section, we will take a brief look at common data center network architecture.
+
+A data center is a facility used to house computer systems and associated components, it usually contains hundreds of thousands devices and links.
+Modern data centers use hierarchical architecture.
+Figure 1 depicts a conventional data center network architecture \cite{gill2011understanding, greenberg2009vl2, herodotou2014scalable}.
+At the bottom layer are racks of servers, typically there are 20 to 40 servers in each rack, and each server in the same rack connects to a Top of Rack (ToR) Switch via a 1 Gbps link.
+Each ToR then connects to a primary and a backup Aggregation Switch (AS) for redundancy.
+ASs are connected to Access Routers (ARs) forming a complete bipartite graph.
+Finally, ARs are connected to Core Routers (CRs).
+
+To limit overheads and to isolate different services, servers are partitioned into virtual LANs (VLANs).
+All links in the data center use Ethernet as link layer protocol and physical connections are a mix of copper and fiber cables.
+In addition to the devices in Figure 1, there may exist other devices like load balancers (LBs) and firewalls.
+
+Modern data center usually employs \textit{Equal Cost MultiPath} (ECMP) routing within the data center for fault tolerance, which means that there are multiple paths from source to destination.
+Thus in this work, we will apply ECMP routing to the simulated network by enabling ECMP routing configurations in NS-3.
+
+% figure
+\begin{figure}
+\centering
+\includegraphics{topology}
+\caption{Conventional Data Center Network Topology}
+\end{figure}
+
+\section{Approach Overview}
+In this section, we will introduce the whole design of our failure detection approach.
+
+Different network device should have different quality of service (QoS).
+Gill et.al \cite{gill2011understanding} have shown the diversity of different devices' failure characteristics.
+Unfortunately, none of the work in Section 2 treats these devices differently.
+We firstly divide network devices into two categories.
+
+\begin{itemize}
+\item \textbf{Imperetative Device.} This category includes servers, ToRs and links between ToRs and servers.
+Typically servers run various user applications and store user data.
+The crash of servers may cause user-perceived faults.
+The crash of a ToR will make servers under it unreachable.
+Also Gill et.al declare that the downtime of ToRs may be very long.
+Thus the failure detection for these devices must be fast enough besides the accuracy requirement.
+
+\item \textbf{Non-imperetative Device.} It includes other routers and switches.
+A single failure of a link or a router does not affect the functionality of a data center because of path redundancy.
+So administrators care more about how effective the detect service is (The ability to identify actually happening failures).
+
+\end{itemize}
+
+% figure
+\begin{figure}
+\centering
+\includegraphics{system}
+\caption{Failure Detection System Architecture}
+\end{figure}
+
+Figure 2 illustrates the entire architecture of our failure detection system.
+It mainly contains two modules.
+The servers failure detection system is autonomous and combines centralized structure with decentralized structure.
+A server can both play the role of a detector and a monitored object.
+Each server is monitored by multiple FD processes installed on different servers for redundancy.
+A server can also monitor a group of servers.
+Once the FD outputs the crash of a server, it will send a crash report message to \textbf{Crash Decider}.
+\textbf{Crash Decider} will determine the final status of this server.
+
+For the detection of non-imperetative devices, \textbf{Traffic Collector} periodically collects traffic data of routers and switches and send telemetry data to \textbf{Traffic Analysis Worker}.
+\textbf{Traffic Analysis Worker} finally generate failure alerts by performing analysis on these data.
+
+\section{Failure Detection Approach}
+In this section, we will discuss the detailed design of different modules of the failure detection system respectively.
+
+\subsection{Failure Detection for servers}
+Failure Detection for servers is responsible for reporting the crash of servers effectively and efficiently.
+Our detection model is based on the assumption that once the server crashes, it never recovers by itself.
+The QoS of failure detection for servers are as follows:
+
+\begin{itemize}
+\item \textbf{Efficiency.} It measures how fast the system can report the crash of the server after it crashes. The system is more efficient if it takes less time to detect a failure.
+\item \textbf{Completeness.} It measures whether the system can detect all the crashed servers. The system is more complete if it rules out fewer true crashed ones.
+\item \textbf{Soundness.} In some scenarios, the behavior of the network may vary.
+For example, message loss and message delay may happen sometimes.
+The detection system should be sound enough to distinguish between such condition and a real crash.
+
+\end{itemize}
+
+\subsubsection{k-detector}
+To meet the requirements mentioned above, this paper proposes a detector model named $k$-detector model which means each server is monitored by $k$ FDs on different servers whereas $k$ is a parameter tuned by users.
+\textbf{Crash Decider} only
+
+\paragraph{Rationale}
+
+\subsubsection{Monitoring Rule Inference}
+
+\subsection{Failure Detection for ToRs}
+
+\subsection{Failure Detection for Links}
+
 \section{Evaluation}
+In this section, we will present how we evaluate the efficiency and effectiveness of our approach as well as the experiments results.
+
+\subsection{Experiments Setup}
 
@@
 
-%ACKNOWLEDGMENTS are optional
 \section{Acknowledgments}
-This work is partially supported by the National High-Technology Research and Development Program of China under Grant No.2014AA01A301.
+This work is partially supported by the National High-Technology Research and Development Program of China (Grant No.2014AA01A301).
 

### 2016-06-27 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing my paper >_<

@@
 
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
 \begin{document}
@@
 
-\title{A Failure Detection approach of Data Center Networks\titlenote{(Produces the permission block, and
+\title{A Failure Detection Approach of Data Center Networks\titlenote{(Produces the permission block, and
 copyright information). For use with
@@
 
-\numberofauthors{8} %  in this sample file, there are a *total*
+%\numberofauthors{8} %  in this sample file, there are a *total*
 % of EIGHT authors. SIX appear on the 'first-page' (for formatting
@@
 \begin{itemize}
-\item \textbf{Imperetative Device.} This category includes servers, ToRs and links between ToRs and servers.
+\item \textbf{Imperative Device.} This category includes servers, ToRs and links between ToRs and servers.
 Typically servers run various user applications and store user data.
@@
 
-\item \textbf{Non-imperetative Device.} It includes other routers and switches.
+\item \textbf{Non-imperative Device.} It includes other routers and switches.
 A single failure of a link or a router does not affect the functionality of a data center because of path redundancy.
@@
 
-\subsection{Failure Detection for servers}
-Failure Detection for servers is responsible for reporting the crash of servers effectively and efficiently.
-Our detection model is based on the assumption that once the server crashes, it never recovers by itself.
-The QoS of failure detection for servers are as follows:
+\subsection{K-detectors Model}
+To detect the crash of servers and ToRs effectively and efficiently, this paper propose a detection model named $K$-detectors model.
+Our detection model is based on the assumption that once the server or ToR crashes, it never recovers by itself.
+The QoS of failure detection are as follows:
 
 \begin{itemize}
-\item \textbf{Efficiency.} It measures how fast the system can report the crash of the server after it crashes. The system is more efficient if it takes less time to detect a failure.
-\item \textbf{Completeness.} It measures whether the system can detect all the crashed servers. The system is more complete if it rules out fewer true crashed ones.
+\item \textbf{Efficiency.} It measures how fast the system can report the crash after it crashes. The system is more efficient if it takes less time to detect a failure.
+\item \textbf{Completeness.} It measures whether the system can detect all the crashed objects. The system is more complete if it rules out fewer true crashed ones.
 \item \textbf{Soundness.} In some scenarios, the behavior of the network may vary.
@@
 
-\subsubsection{k-detector}
-To meet the requirements mentioned above, this paper proposes a detector model named $k$-detector model which means each server is monitored by $k$ FDs on different servers whereas $k$ is a parameter tuned by users.
-\textbf{Crash Decider} only
+In $K$-detectors model, each server is monitored by $K$ FDs on different servers where $K$ is a parameter tuned by users.
+When a FD considers a server crashes, it sends a crash report message to \textbf{Crash Decider}.
+If the output of the FD transforms from suspect to trust, it re-sends a message to revoke the most recent crash report.
+
+\begin{equation}
+S_{s,t}=\left\{
+    \begin{array}{lcl}
+    \text{suspect} & \text{if} & \|CRM_{s,t}\|\geq\left\lfloor(K+1)/2\right\rfloor \\
+
+    \text{trust} && \text{otherwise}
+    \end{array}
+\right.
+\end{equation}
+where $CRM_{s,t}$ denotes the collection of crash report messages for server $s$ until time $t$, $S_{s,t}$ denotes the status of server $s$ at time $t$.
+If \textbf{Crash Decider} receives $\left\lfloor(K+1)/2\right\rfloor$ crash messages of a server, it considers the server to have crashed.
+
+\subsection{Monitoring Rule Inference}
+To form the $K$-detectors model and also to meet QoS to the greatest extent, we propose the following specifications of monitoring relationships among servers:
+\begin{enumerate}
+    \item Each sever monitors $K$ servers. This balances monitor intensity of each server.
+    \item A server cannot monitor itself.
+    \item A server is monitored by $K$ different servers.
+    \item $K-1$ of the $K$ detectors are on the servers at the same rack.
+    \item The monitoring rule should ensure each link covered by heartbeat messages.
+    \item Each rack of servers monitor servers of other racks, which vary from different racks averagely.
+\end{enumerate}
 
 \paragraph{Rationale}
+Intuitively, the use of $K$ FDs is able to adapt to bursty-traffic conditions like message loss because the determination of a failure requires at least $\left\lfloor(K+1)/2\right\rfloor$ FDs' agreement.
+Also, $K$-detectors can prevent crashes of FDs to some extent.
+Theoretically, a failure can still be detected even when $K-\left\lfloor(K+1)/2\right\rfloor=\left\lfloor K/2\right\rfloor$ of its detectors crashed.
 
-\subsubsection{Monitoring Rule Inference}
+On the other hand, the fourth specification above can make the best of locality of LAN, which reduces the probability of degeneration on detection time in turn.
+
+Specification five is the presupposition of link failure detection. It is easy to see that, some links cannot be distinguished from faulty links without this specification.
+
+The last one is an extension of specification five. It is for the consideration of ToRs' detection, we will discuss it in detail in section 5.4.
+
+\subsection{FD Algorithm}
+Our FD algorithm is almost the same as \textit{Chen} FD \cite{chen2002quality} except for some minor changes.
+
+\begin{equation}
+EA_{l+1} \approx \frac{1}{n}(\sum_{i=1}^{n}A_i - \eta s_i)+(l+1)\eta
+\end{equation}
+this formula estimates the expected arriving time of next message, where $s_i$ is the sequence number of heartbeat message, $A_i$ is the receipt time of message $i$, $\eta$ is message send interval.
+Obviously, this formula normalizes each $A_i$ by shifting it backward $\eta s_i$ time units.
+
+After that, we utilize hyperbolic tangent function to model current suspicious level:
+
+\begin{equation} 
+\tau(t_{now}) = |tanh(t_{now}-EA_{l+1})|
+\end{equation}
+suspicious level $\tau(t_{now})$ always ranges from 0 to 1, when $t_{now}$ grows bigger, the suspicious level is closer to 1, which implies a higher failure probability.
+A continuous valued rather than binary valued output decouples the interpretation of failure data from the failure monitoring mechanism, user applications can set their own threshold according to their demands.
 
 \subsection{Failure Detection for ToRs}
+Apart from determination of servers' crashes, \textbf{Crash Decider} is also responsible for failure detection for ToRs.
+If most or even all servers in a rack is viewed as crashed, it is more likely that the top of rack switch crashes rather than the servers.
+
+\begin{equation}
+S_{ToR,t}=\left\{
+    \begin{array}{lcl}
+    \text{suspect} & \text{if} & \|\left\{s|s\in ToR\right\} \cap \left\{s|S_{s,t}=\text{suspect}\right\}\| \\
+    && \geq \alpha \cdot m\\
+    \text{trust} && \text{otherwise}
+    \end{array}
+\right.
+\end{equation}
+where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion to determine failure of a ToR is.
+When \textbf{Crash Decider} finds more than $\alpha \cdot m$ servers under the ToR crash, it will report the crash of ToR rather than these servers.
+The last specification in section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure.
+An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.
+
+To sum up, Algorithm 1 illustrates the pseudo-code for overall detection algorithm of \textbf{Crash Decider}.
+
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+\begin{algorithm}
+	\caption{Detection Algorithm for \textbf{Crash Decider}}
+	%\label{alg0}
+	\begin{algorithmic}[1]
+		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
+		\ENSURE $S_{i,t}$, $i$ is an imperative device
+
+        \FOR{$i \text{ in imperative devices}$}
+            \STATE $S_{i,t_0} \Leftarrow trust$
+        \ENDFOR
+	    \WHILE{$True$}
+            \STATE $List<Integer> failsEachRack \Leftarrow \emptyset$
+            \FOR{each $i$ in Servers}
+                \IF{$\|CRM_{s,t_{now}}\| \geq \left\lfloor(K+1)/2\right\rfloor$}
+                    \STATE $S_{i,t_{now}} \Leftarrow suspect$
+                    \STATE $rackID \Leftarrow getRackID(i)$
+                    \STATE $failsEachRack.get(rackID)++$
+                \ELSE
+                    \STATE $S_{i,t_{now}} \Leftarrow trust$
+                \ENDIF
+            \ENDFOR
+
+            \FOR{each i in ToRs}
+                \IF{$failsEachRack.get(i) \geq \alpha \cdot m$}
+                    \STATE $S_{i,t_{now}} \Leftarrow suspect$
+                \ELSE
+                    \STATE $S_{i,t_{now}} \Leftarrow trust$ 
+                \ENDIF
+            \ENDFOR
+		\ENDWHILE
+	\end{algorithmic}
+\end{algorithm}
+It firstly determines the status of each server (line 6 to 14), and then determines the status of ToRs (line 15 to 21).
 
 \subsection{Failure Detection for Links}
+The failure detection for links is another important part of our detection system, this paper presents the following QoS:
+\begin{itemize}
+  \item \textbf{Precision.} Precision indicates how many suspected links are true failed. 
+  \item \textbf{Completeness.} This measures whether our approach can find all the faulty links.
+  \item \textbf{Discrimination.} Because we will provide a short ranked list of suspected objects, this measures to what degree can our approach distinguish between normal links and faulty links.
+\end{itemize}
+
+The key idea of our approach is to capture network traffic changes as times going on.
+If the network traffic changes significantly compared with traffic in normal conditions, we believe that there exists failures somewhere in the network.
+The insight is that network traffic distribution is associated with routing protocol and monitoring relationships of servers, the drastic changes of traffic probably imply failures.
+
+To collect required traffic data, we simply install \textit{tcpdump} on each router and switch. These data will be sent to \textbf{Traffic Analysis Worker} for further analysis.
+
+In order to model this data analysis problem, this paper proposes a Back Propagation Neural Network (BPNN) based classifier.
+
+\paragraph{Feature Extraction}
+The first step is to extract reasonable features from raw traffic data. To address this issue, we extract $m^2$ features, each of which denotes traffic of one direction. Because there are $m$
 
 \section{Evaluation}
-In this section, we will present how we evaluate the efficiency and effectiveness of our approach as well as the experiments results.
+In this section, we will present how we evaluate our approach in terms of efficiency and effectiveness. Experiments results will also be shown in this section.
 

### 2016-06-28 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing my paper

@@
 
-\item \textbf{Non-imperative Device.} It includes other routers and switches.
+\item \textbf{Non-imperative Device.} It includes links, other routers and switches.
 A single failure of a link or a router does not affect the functionality of a data center because of path redundancy.
@@
 It mainly contains two modules.
-The servers failure detection system is autonomous and combines centralized structure with decentralized structure.
+The servers failure detection system combines centralized with decentralized structures.
 A server can both play the role of a detector and a monitored object.
 Each server is monitored by multiple FD processes installed on different servers for redundancy.
-A server can also monitor a group of servers.
+A server can also monitor a couple of servers.
 Once the FD outputs the crash of a server, it will send a crash report message to \textbf{Crash Decider}.
@@
 
-To collect required traffic data, we simply install \textit{tcpdump} on each router and switch. These data will be sent to \textbf{Traffic Analysis Worker} for further analysis.
+To collect required traffic data, we simply install \textit{tcpdump} on each router and switch. These data will be collected to \textbf{Traffic Analysis Worker} for further analysis.
 
@@
 \paragraph{Feature Extraction}
-The first step is to extract reasonable features from raw traffic data. To address this issue, we extract $m^2$ features, each of which denotes traffic of one direction. Because there are $m$
+The first step is to extract reasonable features from raw traffic data.
+To address this issue, we extract $n^2$ features, each of them denotes traffic of one direction where $n$ denotes the number of racks.
+Obviously, for each rack, there are $n$ different traffic directions (each one corresponds to one rack), so there are $n^2$ directions in total.
+Formally, the traffic feature during a time period
 

### 2016-06-28 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing my paper

@@
 \begin{algorithm}
-	\caption{Detection Algorithm for \textbf{Crash Decider}}
+	\caption{Detection Algorithm of \textbf{Crash Decider}}
 	%\label{alg0}
@@
                     \STATE $rackID \Leftarrow getRackID(i)$
-                    \STATE $failsEachRack.get(rackID)++$
+                    \STATE $failsEachRack.get(rackID)\text{++}$
                 \ELSE
@@
 
-The key idea of our approach is to capture network traffic changes as times going on.
+The key idea of our approach is to capture network traffic changes over time.
 If the network traffic changes significantly compared with traffic in normal conditions, we believe that there exists failures somewhere in the network.
@@
 
-In order to model this data analysis problem, this paper proposes a Back Propagation Neural Network (BPNN) based classifier.
+In order to model this data analysis problem, this paper proposes a Back Propagation Neural Networks (BPNN) based method to compute failure probability of each link.
 
 \paragraph{Feature Extraction}
-The first step is to extract reasonable features from raw traffic data.
-To address this issue, we extract $n^2$ features, each of them denotes traffic of one direction where $n$ denotes the number of racks.
-Obviously, for each rack, there are $n$ different traffic directions (each one corresponds to one rack), so there are $n^2$ directions in total.
-Formally, the traffic feature during a time period
+The first step is to extract rational features from raw traffic data.
+To address this issue, we extract $v \cdot n^2$ features in total.
+$v$ is number of devices (CRs, ARs, ASs), each device has $n^2$ features where $n$ is the number of racks.
+In particular, each feature denotes traffic of one direction.
+Obviously, there are $n$ choices of sources and $n$ choices of destinations, so the total number of possible traffic directions is $n^2$.
+Formally, the traffic features during a time period $\Delta T$ is presented as \boldmath $x$ 
+\unboldmath $=($\boldmath $x_1, x_2, ..., x_v$\unboldmath $)$, \boldmath $x_i$
+\unboldmath $=(x_i^1, x_i^2, ..., x_i^{n^2})$
+where $x_i^j$ stands for direction $j$ traffic of device $i$ in $\Delta T$.
+
+\paragraph{BPNN Model}
+Suppose the number of links is $e$, for each time period $\Delta T$, the output of our model should be
+\boldmath $y$ 
+\unboldmath $=(y_1, y_2, ..., y_e)$, where $y_i$ denotes failure probability of link $i$.
+We apply a BPNN model to localize the faulty link during $\Delta T$.
+As is shown in Figure 3, BPNN is a multi-layer perceptron architecture:
+\begin{figure}
+  \centering
+  \includegraphics{ANN}
+  \caption{Multi-layer Perceptron Architecture}
+\end{figure}
+To reduce the computational work of training, we only set one hidden layer, both the hidden layer neurons and output layer neurons utilize Sigmoid function as the activation function.
+Take the output layer as an example:
+$y_i = Sigmoid(\beta_i - \theta_i)$ where $\theta_i$ is a constant term of the perceptron.
+
+\paragraph{Training of BPNN}
+To train the neural network, we apply the classical error BackPropagation (BP) algorithm \cite{rumelhart1988learning}. BP algorithm is based on gradient descent strategy.
+????? % write BP algorithm?
+
+\paragraph{The Detection Algorithm}
+BPNN model is only able to identify the faulty link during one time unit, in the following part, we will introduce how we can detect multiple faults over time.
+
+First of all, we assume that there are at most one link failure during a time unit ($\Delta T$).
+This assumption is partially supported by the finding proposed by Gill et.
+al.
+They find that on an average, link failures tend to be separated by a period of about one week \cite{gill2011understanding}.
+
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+\begin{algorithm}
+	\caption{\textbf{Traffic Analysis Worker} Algorithm}
+	\begin{algorithmic}[1]
+        \REQUIRE \boldmath $x^t$ \unboldmath$=($\boldmath $x_1^t, x_2^t, ..., x_v^t$\unboldmath $)$
+		\ENSURE $F_i \text{ for } i \in E$
+
+        \STATE $\text{divide traffic data }$\boldmath $x^t$$\text{ into }$\unboldmath $t/\Delta T \text{ chunks}$
+
+        \FOR{$i \in E$}
+            \STATE $F_i \Leftarrow 0$
+        \ENDFOR
+        \FOR{$\text{each data chunk } $ \boldmath $x$}
+        \STATE \boldmath $y$\unboldmath $\Leftarrow BPNN($\boldmath $x$\unboldmath $)$
+            \FOR{$i \in E$}
+                \STATE $F_i \Leftarrow F_i + y_i$
+            \ENDFOR
+        \ENDFOR
+
+        \FOR{\unboldmath $i \in E$}
+            \STATE $F_i \Leftarrow \frac{\Delta T F_i}{t}$
+        \ENDFOR
+        \STATE $\text{sort }$\boldmath $F$\unboldmath$\text{ in descending order}$
+	\end{algorithmic}
+\end{algorithm}
+
+Algorithm 2 shows the algorithm of \textbf{Traffic Analysis Worker}.
+The input of the algorithm is the refined traffic data over time $T$.
+Traffic data is then divided into chunks and each chunk represents traffic data of one time unit $\Delta T$ (line 1).
 

### 2016-06-28 src/core/LinkFailureDetector.java

@@ -84,17 +84,41 @@ public class LinkFailureDetector {
 		ClassifyModeller cm = new ClassifyModeller();
 		List<List<Item>> res = cm.classify();
 		
+		List<Item> fs = new ArrayList<Item>();
+		
+		for(int i=0; i<res.size()-1; i++) {
+			for(int j=0; j<res.get(i).size(); j++) {
+				Item item = res.get(i).get(j);		
+				if(i == 0) {
+					fs.add(item);
+				}
+				else {
+					fs.get(j).value += item.value;
+				}
+			}
+		}
+		
+		Util.normalize(fs);
+		Collections.sort(fs);
+		
+		for(Item item : fs) {	
+			System.out.println(item);
+		}
+			
 		/*
 		for(int i=0; i<res.size(); i++) {
+			System.out.println(i+3);
 			for(Item item : res.get(i))
 				System.out.println(item.item_name + ": " + item.value);
 			System.out.println();
-		} */
+		} 
+		*/
 		
-		
+		/*
 		for(int i=1; i<res.size(); i++) {
 			System.out.println(Evaluator.discrimination(res.get(i)));
-		}
+		} */
+		
 		//System.out.println(Evaluator.discrimination(res.get(i), 21));
 	
 	}
@@ -124,7 +148,7 @@ public class LinkFailureDetector {
 		LinkFailureDetector lfd = new LinkFailureDetector();
 		// lfd.try_it();
 		
-		String mark = "dump-2-1";
+		String mark = "dump-3-5";
 		lfd.detect("z://",
 				"z://LinkCrashDump//",
 				mark);

### 2016-06-28 src/ml/ClassifyModeller.java

@@ -65,7 +65,7 @@ public class ClassifyModeller {
 				//System.out.print(class_mapping.get(j) + ": " + pro[j] + "	");
 			}
 			
-			Collections.sort(list);
+			//Collections.sort(list);
 			ress.add(list);
 		} // end for
 

### 2016-06-28 src/util/Item.java

@@ -19,4 +19,19 @@ public class Item implements Comparable {
 		return 1;
 	}
 	
+	@Override
+	public int hashCode() {
+		return item_name.hashCode();
+	}
+	
+	@Override
+	public boolean equals(Object o) {
+		Item item = (Item) o;
+		return item_name.equals(item.item_name);
+	}
+	
+	@Override
+	public String toString() {
+		return this.item_name + ": " + this.value;
+	}
 }

### 2016-06-28 src/util/Util.java

@@ -9,6 +9,19 @@ import java.util.*;
 
 public class Util {
 	
+	public static void normalize(List<Item> list) {
+		double total = 0;
+		for(Item item : list) 
+			if(!item.item_name.equals("normal"))
+				total += item.value;
+		
+		for(Item item : list) 
+			if(item.item_name.equals("normal"))
+				item.value = 0;
+			else
+				item.value /= total;	
+	}
+	
 	public static double residual(List<Item> list1, List<Item> list2) {
 		double res = 0;
 		for(Item i1 : list1) {

### 2016-07-02 SIG Proceedings Template-Jan2015 Zip/paper.tex
continue writing my paper
write paper && modify code

@@
 %
+\numberofauthors{2}
 \author{
@@
        \affaddr{Shanghai Jiao Tong University}\\
-       \affaddr{Wallamaloo, New Zealand}\\
+       \affaddr{Shanghai, China}\\
        \email{knshen@sjtu.edu.cn}
 % 2nd. author
-\alignauthor Charles Palmer\\
-       \affaddr{Palmer Research Laboratories}\\
-       \affaddr{8600 Datapoint Drive}\\
-       \affaddr{San Antonio, Texas 78229}\\
-       \email{cpalmer@prl.com}
+\alignauthor
+????\titlenote{Dr.~Trovato insisted his name be first.}\\
+       \affaddr{School of Software}\\
+       \affaddr{Shanghai Jiao Tong University}\\
+       \affaddr{Shanghai, China}\\
+       \email{????@sjtu.edu.cn}
 }
@@
 % number that will appear in the \additionalauthors section.
+\maketitle
 
-\maketitle
 \begin{abstract}
@@
 
-\keywords{ACM proceedings; \LaTeX; text tagging}
+\keywords{Failure detection; Quality of Service; Data center networks}
 
@@
 Data center.
-The rest of this paper is organized as follows. Section 2 discusses related work,
+
+The rest of the paper is organized as follows.
+Section 2 discusses related work.
+Section 3 presents data center networks architecture.
+Section 4 provides an overview of our approach, while the details are described in Section 5.
+The experimental evaluation along with experiments results is presented in Section 6.
+Finally, Section 7 concludes this paper.
 
@@
 Modern data center usually employs \textit{Equal Cost MultiPath} (ECMP) routing within the data center for fault tolerance, which means that there are multiple paths from source to destination.
-Thus in this work, we will apply ECMP routing to the simulated network by enabling ECMP routing configurations in NS-3.
+Thus in this work, we will apply ECMP routing to the simulated network by enabling ECMP routing configurations in ns-3.
 
@@
 Different network device should have different quality of service (QoS).
-Gill et.al \cite{gill2011understanding} have shown the diversity of different devices' failure characteristics.
+Gill et al.
+\cite{gill2011understanding} have shown the diversity of different devices' failure characteristics.
 Unfortunately, none of the work in Section 2 treats these devices differently.
@@
 The crash of a ToR will make servers under it unreachable.
-Also Gill et.al declare that the downtime of ToRs may be very long.
+Also Gill et al.
+declare that the downtime of ToRs may be very long.
 Thus the failure detection for these devices must be fast enough besides the accuracy requirement.
@@
     \begin{array}{lcl}
-    \text{suspect} & \text{if} & \|CRM_{s,t}\|\geq\left\lfloor(K+1)/2\right\rfloor \\
+    \text{suspect} & \text{if} & |CRM_{s,t}|\geq\left\lfloor(K+1)/2\right\rfloor \\
 
@@
     \item The monitoring rule should ensure each link covered by heartbeat messages.
-    \item Each rack of servers monitor servers of other racks, which vary from different racks averagely.
+    \item Each rack monitors servers of other racks which vary from different racks averagely.
 \end{enumerate}
 
-\paragraph{Rationale}
-Intuitively, the use of $K$ FDs is able to adapt to bursty-traffic conditions like message loss because the determination of a failure requires at least $\left\lfloor(K+1)/2\right\rfloor$ FDs' agreement.
+\subsubsection*{Rationale}
+\quad Intuitively, the use of $K$ FDs is able to adapt to bursty-traffic conditions like message loss because the determination of a failure requires at least $\left\lfloor(K+1)/2\right\rfloor$ FDs' agreement.
 Also, $K$-detectors can prevent crashes of FDs to some extent.
@@
 
-The last one is an extension of specification five. It is for the consideration of ToRs' detection, we will discuss it in detail in section 5.4.
+The last one is an extension of specification five. It is for the consideration of ToRs' detection, we will discuss it in detail in Section 5.4.
 
 \subsection{FD Algorithm}
-Our FD algorithm is almost the same as \textit{Chen} FD \cite{chen2002quality} except for some minor changes.
+FD algorithm is used to decide the status of one monitored object by one FD. Our FD algorithm is almost the same as \textit{Chen} FD \cite{chen2002quality} except for some minor changes.
 
@@
 Apart from determination of servers' crashes, \textbf{Crash Decider} is also responsible for failure detection for ToRs.
-If most or even all servers in a rack is viewed as crashed, it is more likely that the top of rack switch crashes rather than the servers.
+If most or even all servers in a rack is reported crash by FDs of other racks, it is more likely that the top of rack switch crashes rather than the servers.
 
@@
     \begin{array}{lcl}
-    \text{suspect} & \text{if} & \|\left\{s|s\in ToR\right\} \cap \left\{s|S_{s,t}=\text{suspect}\right\}\| \\
+    \text{suspect} & \text{if} & |\left\{s|s\in ToR\right\} \cap \left\{s|S_{s,t}=\text{suspect}\right\}| \\
     && \geq \alpha \cdot m\\
@@
 \end{equation}
-where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion to determine failure of a ToR is.
-When \textbf{Crash Decider} finds more than $\alpha \cdot m$ servers under the ToR crash, it will report the crash of ToR rather than these servers.
-The last specification in section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure.
+where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion is to determine failure of a ToR.
+When \textbf{Crash Decider} gets more than $\alpha \cdot m$ crash report messages of servers under the ToR crash, it will report the crash of ToR.
+The last specification in Section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure.
 An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.
@@
         \FOR{$i \text{ in imperative devices}$}
-            \STATE $S_{i,t_0} \Leftarrow trust$
+            \STATE $S_{i,t_0} \leftarrow trust$
         \ENDFOR
 	    \WHILE{$True$}
-            \STATE $List<Integer> failsEachRack \Leftarrow \emptyset$
+            \STATE $List<Integer> failsEachRack \leftarrow \emptyset$
             \FOR{each $i$ in Servers}
-                \IF{$\|CRM_{s,t_{now}}\| \geq \left\lfloor(K+1)/2\right\rfloor$}
-                    \STATE $S_{i,t_{now}} \Leftarrow suspect$
-                    \STATE $rackID \Leftarrow getRackID(i)$
+                \STATE $rackID \leftarrow getRackID(i)$
+                \IF{$|CRM_{i,t_{now}}| \geq \left\lfloor(K+1)/2\right\rfloor$}
+                    \STATE $S_{i,t_{now}} \leftarrow suspect$
+                \ELSE
+                    \STATE $S_{i,t_{now}} \leftarrow trust$
+                    \IF{$\text{only one CRM coming from other rack}$}
                     \STATE $failsEachRack.get(rackID)\text{++}$
-                \ELSE
-                    \STATE $S_{i,t_{now}} \Leftarrow trust$
+                    \ENDIF
                 \ENDIF
@@
                 \IF{$failsEachRack.get(i) \geq \alpha \cdot m$}
-                    \STATE $S_{i,t_{now}} \Leftarrow suspect$
+                    \STATE $S_{i,t_{now}} \leftarrow suspect$
                 \ELSE
-                    \STATE $S_{i,t_{now}} \Leftarrow trust$
+                    \STATE $S_{i,t_{now}} \leftarrow trust$
                 \ENDIF
@@
 \end{algorithm}
-It firstly determines the status of each server (line 6 to 14), and then determines the status of ToRs (line 15 to 21).
+It firstly determines the status of each server (line 6 to 16), and then determines the status of ToRs (line 17 to 23).
+When detecting server failures, \textbf{Crash Decider} also records necessary information to find potential ToR crashes (line 12 to 13).
 
@@
 The insight is that network traffic distribution is associated with routing protocol and monitoring relationships of servers, the drastic changes of traffic probably imply failures.
+For example, if the network topology is just as Figure 1 shows, when the link between the leftmost AR and the leftmost AS fails, the traffic on the leftmost AR will decrease and the rightmost AR's traffic will increase according to ECMP routing.
 
@@
 
-\paragraph{Feature Extraction}
-The first step is to extract rational features from raw traffic data.
+\subsubsection*{Feature Extraction}
+\quad The first step is to extract rational features from raw traffic data.
 To address this issue, we extract $v \cdot n^2$ features in total.
@@
 
-\paragraph{BPNN Model}
-Suppose the number of links is $e$, for each time period $\Delta T$, the output of our model should be
+\subsubsection*{BPNN Model}
+\quad Suppose the number of links is $e$, for each time period $\Delta T$, the output of our model should be
 \boldmath $y$
@@
 
-\paragraph{Training of BPNN}
-To train the neural network, we apply the classical error BackPropagation (BP) algorithm \cite{rumelhart1988learning}. BP algorithm is based on gradient descent strategy.
-????? % write BP algorithm?
+\subsubsection*{Training of BPNN}
+\quad To train the neural network, we apply the classical error BackPropagation (BP) algorithm \cite{rumelhart1988learning}. BP algorithm is based on gradient descent strategy.% write BP algorithm?
 
-\paragraph{The Detection Algorithm}
-BPNN model is only able to identify the faulty link during one time unit, in the following part, we will introduce how we can detect multiple faults over time.
+To get train data, we manually disable links to simulate real link failures.
+To be specific, each time we disable one link for some time.
+After that, we collect dump data from each router and switch, extracting direction features just as mentioned above.
+The next step is to split the traffic data into different chunks, with each chunk representing the traffic data within one time unit ($\Delta T$).
+Each traffic chunk forms one train instance.
+
+\subsubsection*{The Detection Algorithm}
+\quad BPNN model is only able to identify the faulty link during one time unit, in the following part, we will introduce how we can detect multiple faults over time.
 
 First of all, we assume that there are at most one link failure during a time unit ($\Delta T$).
-This assumption is partially supported by the finding proposed by Gill et.
-al.
+This assumption is partially supported by the finding proposed by Gill et al.
 They find that on an average, link failures tend to be separated by a period of about one week \cite{gill2011understanding}.
@@
 
-        \STATE $\text{divide traffic data }$\boldmath $x^t$$\text{ into }$\unboldmath $t/\Delta T \text{ chunks}$
+        \STATE $\text{divide traffic data }$\boldmath $x^t$$\text{ into }$\unboldmath $\left\lfloor t/\Delta T \right\rfloor \text{ chunks}$
 
         \FOR{$i \in E$}
-            \STATE $F_i \Leftarrow 0$
+            \STATE $F_i \leftarrow 0$
         \ENDFOR
         \FOR{$\text{each data chunk } $ \boldmath $x$}
-        \STATE \boldmath $y$\unboldmath $\Leftarrow BPNN($\boldmath $x$\unboldmath $)$
+        \STATE \boldmath $y$\unboldmath $\leftarrow BPNN($\boldmath $x$\unboldmath $)$
             \FOR{$i \in E$}
-                \STATE $F_i \Leftarrow F_i + y_i$
+                \STATE $F_i \leftarrow F_i + y_i$
             \ENDFOR
@@
         \FOR{\unboldmath $i \in E$}
-            \STATE $F_i \Leftarrow \frac{\Delta T F_i}{t}$
+            \STATE $F_i \leftarrow \frac{\Delta T F_i}{t}$
         \ENDFOR
@@
 Algorithm 2 shows the algorithm of \textbf{Traffic Analysis Worker}.
-The input of the algorithm is the refined traffic data over time $T$.
-Traffic data is then divided into chunks and each chunk represents traffic data of one time unit $\Delta T$ (line 1).
+The input of the algorithm is the refined time series traffic data over time $T$.
+Firstly, traffic data is divided into chunks.
+Each chunk represents a time unit $\Delta T$ (line 1) of traffic.
+The last chunk will be dropped if its time period is less than $\Delta T$.
+For each of traffic data chunk, we utilize the trained BPNN model to compute failure score of links during this time unit.
+The final failure score over $t$ is computed as the arithmetic mean of failure scores of all time units (line 5 to 13).
+This solution inevitably benefits the early happened faulty links.
+For example, when there are only one faulty links in the network, the failure score of the sole faulty link will be very high, which in turn makes its final failure score higher.
+However, it does not matter because we care more about whether it can find as many failures rather than the ranking.
 
@@
 
-\subsection{Experiments Setup}
+\subsection{Experimental Settings}
+To build up a data center network, we deploy ns-3 on PC.
+ns-3 is a discrete-event network simulator for Internet systems, targeted primarily for research and educational use \cite{henderson2008network}.
+we install ns-3 on single PC with 2 cores, 3.4 GHz CPU and 4GB RAM.
+The version of ns-3 we use is ns-3.24.
+
+We set up a simulated data center network following the topology in Figure 1.
+There are a total of 120 servers (20 servers $\times$ 6 racks), 14 routers and switches and 140 links.
+For each link, data rate is 100 Mbps, delay is 100 ms.
+
+\subsection{Research Questions}
+The objective of our experiments is to validate the effectiveness and efficiency of the proposed approach compared with baselines. For this purpose, we set up the following research questions:
+
+\subsubsection*{RQ1: How about the QoS of K-detectors model?}
+\quad RQ1 evaluates QoS of failure detection for servers. To answer this question, we firstly set four metrics \cite{chen2002quality} corresponding to the QoS in Section 5.1.
+\begin{itemize}
+  \item \textbf{Average Detection Time ($AT_D$)} is the average time that elapses from the crash of a server until the crash is reported.
+  \begin{equation}
+    AT_D = \frac{\sum_i(T_{D,i} - T_{C,i})}{n}
+  \end{equation}
+  where $n$ is the number of detected crashes, $T_{D,i}$ is the detection time of $i$th crash $i$, $T_{C,i}$ is the crash time of $i$th crash.
+
+  \item \textbf{Average Mistake Rate ($AR_M$)} measures the average rate at which a FD suspects a correct object.
+It equals the number of such mistakes per unit of time.
+Suppose Figure 4 depicts the monitoring of the object in one time unit, the mistake rate of this FD is two.
+\begin{figure}
+  \centering
+  \includegraphics{metric}
+  \caption{Average Mistake Rate}
+\end{figure}
+
+  \item \textbf{Query Accuracy Probability ($P_A$)} is the probability that the detection system outputs the correct results when queried at a random time.
+
+  \item \textbf{Number of Undetected Crashes} measures the number of ignored real crash servers.
+\end{itemize}
+
+We compare our work with the traditional hierarchical architecture \cite{felber1999failure} in terms of the metrics above.
+
+\subsubsection*{RQ2: Can K-detectors model benefit ToR crash detection?}
+\quad The evaluation of failure detection for ToRs is almost the same as servers. We will evaluate the impact of different values of $\alpha$.
+
+\subsubsection*{RQ3: How about the QoS of BPNN based model?}
+\quad This RQ evaluates whether the proposed approach is more effective in detecting link failures. We make another three metrics:
+\begin{itemize}
+    \item \textbf{Precision@k.} We make the use of this metric in order to evaluate to what degree the detection is accurate.
+This metric is appropriate because it does not take into account the positions in the list which caters to our requirements \cite{mogotsi2010christopher}.
+    \begin{equation}
+        precision@k = \frac{1}{n}\sum_{i=1}^n \frac{fail_{i,k}}{k}
+    \end{equation}
+    where $fail_{i,k}$ denotes the number of true failures for failure event $i$ in the top $k$ returned results.
+$n$ is the number of failure events, $k$ equals to the number of true failures.
+A perfect result is all the $k$ failures are ranked at the top $k$ positions.
+
+    \item \textbf{MRR.} We also make use of Mean Reciprocal Rank (MRR), which is a statistic measure for evaluating a process that produces a ranked list to a sample of queries, the list contains items ordered by probabilities \cite{radev2002evaluating}.
+It is the average multiplicative inverse of the rank of the first faulty link:
+        \begin{equation}
+            MRR = \frac{1}{n}\sum_{i=1}^n \frac{1}{rank_i}
+        \end{equation}
+
+    \item \textbf{Discriminative Significance} (DS). DS is based on the notion of entropy. Entropy is a measure of unpredictability of information content \cite{shannon2001mathematical}.
+        \begin{equation}
+            DS = -\sum_{i=1}^e F_i \cdot log_2 F_i
+        \end{equation}
+        where $F_i$ is a normalized failure score of link $i$. A smaller DS implies that the results of ranked list is more determinate, which makes it easier for further troubleshooting.
+
+\end{itemize}
+
+We will compare this part of our approach with the work of Herodotou et al. \cite{herodotou2014scalable}.
+
+\subsection{Experiments Results}
+
+\subsubsection*{RQ1: QoS of K-detectors Model}
+\quad We evaluate our approach in the presence of different degrees of message loss and server crashes.
+To be fair, FD parameters of all the methods are set to the same: $\tau_m=0.001$, slide window size $n=100$.
+Heartbeat message send interval $\eta$ is 100 ms.
+The whole application is run for 1 min.
+
+\begin{figure}
+  \centering
+  \begin{tabular}{c}
+  \includegraphics[scale=0.7]{r1} \\
+  \includegraphics[scale=0.7]{r2}
+  \end{tabular}
+  \caption{Effect of Message Loss on $P_A$ and $AM_R$}
+\end{figure}
+Figure 5 depicts $P_A$ and $AR_M$ of K-detectors and hierarchical architecture under different number of message loss without server crashes.
+Both the time and channel of message loss is chosen randomly.
+When loss rate is under 1\%, 5-detectors has about an 8.2\% improvement in $P_A$ compared with hierarchical architecture.
+When loss rate is over 0.6\%, 5-detectors makes more mistakes than others, this is probably because other methods make mistakes with relatively longer time.
+In a nutshell, with a larger parameter $K$, our approach behaves better in the presence of normal message loss.
+However, it cannot maintain with the increasing number of message loss.
+
+\begin{figure}
+  \centering
+  \begin{tabular}{c}
+  \includegraphics[scale=0.7]{r3} \\
+  \includegraphics[scale=0.7]{r4} \\
+  \includegraphics[scale=0.7]{r5} \\
+  \end{tabular}
+  \caption{Effect of Crashes on $P_A$, $AR_M$ and $AT_D$}
+\end{figure}
+Subsequently, we investigate it when there exists server crashes.
+We set message loss rate to 0.1\%, both the time and server ID of crashes are selected randomly.
+As is shown in Figure 6, 5-detectors has a better $P_A$ and $AR_M$ than others in most cases.
+In terms of $AD_T$, a smaller $K$ results in a quicker detection because it needs fewer FDs to reach an agreement.
+In general, $AD_T$ of 5-detectors has a 22.4\% increase, while 2-detectors only has a 7.3\% increase compared with hierarchical architecture.
+Figure 7 shows the number of undetected crashes, hierarchical architecture tends to behave worse than K-detectors, which reveals the \textit{Single Point of Failure} problem of hierarchical architecture.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.7]{r6}
+  \caption{Number of Undetected Crash Servers}
+\end{figure}
+
+\subsubsection*{RQ2: ToR crash Detection}
+\quad To answer this question,
+
+The drawback of our approach is that once occurring ToR failures, we cannot detect server crashes within the rack before the ToR recovering.
+
+\subsubsection*{RQ3: QoS of BPNN Based Model?}
+\quad To answer this question, we wants to firstly explain why we select BPNN rather other popular classifiers.
+We select 3 other algorithms including Decision Tree (C4.5) \cite{quinlan2014c4}, Bayesian Networks (BN) \cite{jensen1996introduction} and Support Vector Machine (SVM) \cite{scholkopf1999advances}.
+We apply these algorithms to train data by 10-fold cross-validation.
+Results are all shown in Table 1.
+Obviously BPNN outperforms other algorithms.
+
+\begin{table}
+    \centering
+    \caption{Results of Different Classifiers}
+    \begin{tabular}{|c|c|c|c|} \hline
+        \textbf{Classifier} & \textbf{Precision} & \textbf{Recall} & \textbf{F-Measure} \\ \hline
+        \hline
+        \textbf{BPNN} & 98.8\% & 98.8\% & 98.8\% \\ \hline
+        \textbf{C4.5} & 96.4\% & 96.3\% & 96.3\% \\ \hline
+        \textbf{BN} & 96.9\% & 96.6\% & 96.7\% \\ \hline
+        \textbf{SVM} & 96.9\% & 96.6\% & 96.7\% \\ \hline
+    \end{tabular}
+\end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.7]{precision} \\
+  \caption{Precision@k of Different Failure Group Size}
+\end{figure}
+
+Empirically, parameters for BPNN is set as follows: learning rate equals 0.3, number of iterations equals 500, momentum equals 0.2, number of neurons at the hidden layer is $(\# attributes + \# classes) / 2$, $\Delta T = 1 $ s.
+The selection of $\Delta T$ is a tradeoff, when $\Delta T$ grows bigger, it may contain multiple failures which violates our assumption, while a smaller $\Delta T$ may add more occasionality to traffic data.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.7]{mrr} \\
+  \caption{MRR of Different Failure Group Size}
+\end{figure}
+
+We manually make some link failures by disabling links in ns-3, we make 5 random failure events for different size of failure group respectively.
+Both the link ID and failure time are selected randomly.
+As Gill et al.
+finds that link failures tend to be isolated \cite{gill2011understanding}.
+Only 41\% of the link failure groups contain more than one faults, only 10\% contain more than four faults.
+Consequently we only make failure events whose failure group size is no more than four.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.7]{ds} \\
+  \caption{DS of Different Failure Group Size}
+\end{figure}
+
+Figure 8,9 and 10 show the results of out experiments.
+Our approach has a better performance in terms of percision@k and MRR.
+In particular, there is an at least 73.3\% precision@k performance, which indicates 73.3\% of the failures can be found at the most top of the suspects averagely.
+
+On the other hand, there is a huge improvement in terms of DS.
+The approach proposed by Herodotou et al.
+tends to assign a wider range of failure scores to multiple links, while our approach is better at finding the relevant links.
+It mainly stems from the fact that our approach is based on a multi-layer perceptron architecture, it can precisely capture the characteristic of each link failure.
+But one of the drawbacks of our approach is that it requires much data and time to train BPNN offline to ensure its generalization ability, it cannot adapt to network topology changes as well.
 
 \section{Conclusions}
-This paper proposes a failure detector model for data center networks.
+In this paper, we described a complete failure detection approach for data center networks which leverages data mining techniques. 
 %\end{document}  % This is where a 'short' article might terminate
@@
 \section{Acknowledgments}
-This work is partially supported by the National High-Technology Research and Development Program of China (Grant No.2014AA01A301).
+This work is partially supported by the National High-Technology Research and Development Program of China under Grant No.2014AA01A301.
 

### 2016-07-02 src/core/LinkFailureDetector.java

@@ -73,7 +73,7 @@ public class LinkFailureDetector {
 		//System.out.println();
 	}
 
-	public void detect(String train_dump_dir, String test_dump_dir, String mark) throws Exception {	
+	public List<Item> detect(String train_dump_dir, String test_dump_dir, String mark) throws Exception {	
 		// load train data
 		//dataConstructor(train_dump_dir, "link", true);	
 		// ArffMaker.make("train.arff", instances, classes, class_values); 
@@ -101,10 +101,11 @@ public class LinkFailureDetector {
 		Util.normalize(fs);
 		Collections.sort(fs);
 		
+		/*
 		for(Item item : fs) {	
 			System.out.println(item);
-		}
-			
+		}*/
+		
 		/*
 		for(int i=0; i<res.size(); i++) {
 			System.out.println(i+3);
@@ -120,7 +121,7 @@ public class LinkFailureDetector {
 		} */
 		
 		//System.out.println(Evaluator.discrimination(res.get(i), 21));
-	
+		return fs;	
 	}
 	
 	public void try_it() throws IOException {
@@ -144,14 +145,44 @@ public class LinkFailureDetector {
 		}
 	}
 
+	public void run() throws Exception {
+		List<List<String>> faults = new ArrayList<List<String>>();
+		faults.add(Arrays.asList("link2-8", "link4-9", "link5-10", "link0-5"));
+		faults.add(Arrays.asList("link3-7", "link5-11", "link0-5", "link4-10"));
+		faults.add(Arrays.asList("link2-8", "link1-2", "link0-3", "link4-10"));
+		faults.add(Arrays.asList("link0-3", "link0-2", "link1-5", "link4-9"));
+		faults.add(Arrays.asList("link2-8", "link0-2", "link0-3", "link3-6"));
+		int k = 4;
+		
+		//////////////////////////////////////////
+		List<Double> precisions = new ArrayList<Double>();
+		List<Integer> mrrs = new ArrayList<Integer>();
+		List<Double> ds = new ArrayList<Double>();
+		
+		for (int i = 1; i <= 5; i++) {
+			LinkFailureDetector lfd = new LinkFailureDetector();
+			String mark = "dump-" + k + "-" + i;
+			List<Item> res = lfd.detect("z://",
+					"z://LinkCrashDump//",
+					mark);
+
+			precisions.add(Evaluator.precision_k(res, k, faults.get(i-1)));
[…]

### 2016-07-02 src/core/ServerFailureDetector.java

@@ -64,6 +64,8 @@ public class ServerFailureDetector {
 		br.close();
 	}
 	
+	Map<Integer, List<TimePeriod>> raw_reports = new HashMap<Integer, List<TimePeriod>>();
+	
 	public Map<Integer, List<TimePeriod>> detect(int K, boolean haveLoss, double loss_rate) throws IOException {
 		/**
 		 * i: time periods that report crash of node i 
@@ -81,6 +83,7 @@ public class ServerFailureDetector {
 			// i: slave (monitorable object)
 			// crash report for the server i
 			List<TimePeriod> crash_report = new ArrayList<TimePeriod>();
+			List<TimePeriod> raw_report = new ArrayList<TimePeriod>();
 			
 			List<List<TimePeriod>> ress = new ArrayList<List<TimePeriod>>();
 			for(int master : alr.send_rule.get(i)) {
@@ -88,8 +91,9 @@ public class ServerFailureDetector {
 				ress.add(res);
 			}
 				
-			for(double time = 2; time <= end_time; time += time_unit) {
+			for(double time = 2; time <= end_time; time += time_unit) {			
 				int alerts = 0;
+				int detector_id = -1;
 				for(int k = 0; k < ress.size(); k++) {
 					// k = 0,1,2
 					int master_id = alr.send_rule.get(i).get(k);
@@ -99,10 +103,23 @@ public class ServerFailureDetector {
 							Util.isInPeriod(ress.get(k), time)) {
 						//System.out.println(master_id + " report crash of " + i + " at time: " + time);
 						alerts++;
+						detector_id = master_id;
 					}
 						
 				}
-				
+				if(alerts == 1 && Util.getRackIdByServerId(detector_id) != Util.getRackIdByServerId(i)) {
+					if(raw_report.size() == 0)
+						raw_report.add(new TimePeriod(time, time));
+					else {
+						if((time - raw_report.get(raw_report.size()-1).end) > 1.1 * time_unit) {
+							raw_report.add(new TimePeriod(time, time));
+						}
+						else {
+							raw_report.get(raw_report.size()-1).end = time;
+						}
+					}
+				}
+					
 				if(alerts >= (K+1) / 2) {
 					// server i is decided to be crash !!!	
 					if(crash_report.size() == 0)
[…]

### 2016-07-02 src/crash/DeviceCrashMaker.java

@@ -11,6 +11,10 @@ class Fault {
 		this.server_id = si;
 		this.time = time;
 	}
+	
+	public String toString() {
+		return server_id + " " + time;
+	}
 }
 
 public class DeviceCrashMaker {
@@ -32,7 +36,8 @@ public class DeviceCrashMaker {
 			double time = Math.random() * (end - start) + start;
 			events.add(new Fault(si, time));
 		}
-		write(events);
+		System.out.println(events);
+		//write(events);
 	}
 
 	private static void write(List<Fault> events) throws IOException {

### 2016-07-02 src/evaluation/Evaluator.java

@@ -72,7 +72,46 @@ public class Evaluator {
 		return res / corr_freq_all.size();
 	}
 	
-	
+	public static double avgQueryAccuracyPro4ToR(Map<Integer, List<TimePeriod>> alerts, Map<Integer, Double> crashes) {
+		List<Integer> corr_freq_all = new ArrayList<Integer>();
+		
+		int total_time_units = (int)((end_time - 2) / time_unit);
+		/////////////
+		for(int i=0; i<=5; i++) {
+			int correct_frequent = 0;
+			if(!crashes.containsKey(i)) {
+				// no crash
+				int wrong = 0;
+				if(alerts.containsKey(i))
+					for(TimePeriod tp : alerts.get(i)) 
+						wrong += (int)((tp.end - tp.begin) / time_unit);
+				correct_frequent = total_time_units - wrong;
+			}
+			else {
+				// crash at sometime
+				double crash_time = crashes.get(i);
+				if(alerts.containsKey(i)) {
+					for(TimePeriod tp : alerts.get(i)) {
+						if(tp.begin <= crash_time && crash_time <= tp.end)
+							correct_frequent += (int)((tp.end - crash_time) / time_unit);
+						else if(crash_time <= tp.begin)
+							correct_frequent += (int)((tp.end - tp.begin) / time_unit);
+					}
+				}
+			}
+			
+			// for the node i:
+			corr_freq_all.add(correct_frequent);
+		}
+		
+		double res = 0;
+		for(int freq : corr_freq_all) {
+			res += freq / (double)total_time_units;
+		}
+		
+		return res / corr_freq_all.size();
+	}
+
 	public static double faultCrashReportRate(Map<Integer, List<TimePeriod>> alerts, Map<Integer, Double> crashes) {
 		// number of faulty crash reports per second for all monitorable objects
 		double mistakes = 0;
@@ -89,6 +128,22 @@ public class Evaluator {
 		return mistakes / (end_time - 2);
 	}
 
+	public static double faultCrashReportRate4ToR(Map<Integer, List<TimePeriod>> alerts, Map<Integer, Double> crashes) {
+		double mistakes = 0;
+		
+		for(int i=0; i<=5; i++) {
+			if(!alerts.containsKey(i))
+				continue;
+			for(TimePeriod tp : alerts.get(i)) {
+				if(!isCrashNow(i, tp.begin, crashes)) {
+					mistakes++;
+				}
+			}
+		}
+		
[…]

### 2016-07-02 src/parser/DumpAnalyzer.java

@@ -8,7 +8,7 @@ import util.Util;
 
 public class DumpAnalyzer {
 	// parameters:
-	public static final String rule_path = "z://ruleFile//rule-5.txt";
+	public static final String rule_path = "z://ruleFile//rule-3.txt";
 	
 	public static String dir;
 

### 2016-07-02 src/relatedWork/hierarchy/HierarchyServerDetector.java

@@ -133,15 +133,17 @@ public class HierarchyServerDetector extends ServerFailureDetector {
 	}
 
 	public void run() throws IOException {
-		int crash_num[] = new int[]{1,5,10,15,20,25,30,35,40,45,50,55,60};
-		for(int k : crash_num) {
+		double rates[] = new double[]{0.012, 0.014, 0.016, 0.018, 0.02, 0.025 ,0.03 ,0.035 ,0.04};
+
+		for(double rate : rates) {
 			HierarchyServerDetector hsd = new HierarchyServerDetector(
-					"z://serverCrashDump//hie-" + k + "//", 
-					true,
-					"z://crashFile//server-crash-" + k + ".txt");
+					"z://serverCrashDump//hie-0", 
+					false,
+					"z://crashFile//server-crash-" + ".txt");
 			//// enable message loss? loss rate?
-			Map<Integer, List<TimePeriod>> alerts = hsd.detectInHierarchy(true, 0.001);
-			System.out.println(k + ":");
+			Map<Integer, List<TimePeriod>> alerts = hsd.detectInHierarchy(true, rate);
+			
+			System.out.println("rate: " + rate);
 			System.out.println("avg query accurate pro: " + Evaluator.avgQueryAccuracyPro(alerts, hsd.crashes));
 			System.out.println("avg mistake rate: " + Evaluator.faultCrashReportRate(alerts, hsd.crashes));
 			System.out.println("avg detection time: " + Evaluator.avgDetectionTime(alerts, hsd.crashes));

### 2016-07-02 src/relatedWork/kdd2014/AzureLocator.java

@@ -3,6 +3,7 @@ package relatedWork.kdd2014;
 import java.util.*;
 import java.io.*;
 
+import evaluation.Evaluator;
 import util.BiTreeNode;
 import util.Item;
 import util.Route;
@@ -207,50 +208,75 @@ public class AzureLocator {
 
 	}
 
-	public void rank(List<Double> fail_score) {
+	public List<Item> rank(List<Double> fail_score) {
 		double total_score = 0;
-		for(double score : fail_score) {
+		for (double score : fail_score) {
 			total_score += score;
-		
+
 		}
 
 		List<Item> items = new ArrayList<Item>();
-		for(int i = 0; i < edges.size(); i++) {
-			items.add(new Item("link" + edges.get(i), fail_score.get(i)));
+		for (int i = 0; i < edges.size(); i++) {
+			items.add(new Item("link" + edges.get(i), fail_score.get(i) / total_score));
 		}
-		
+
 		Collections.sort(items);
 		
-		System.out.println("total: " + total_score);	
-		
-		for(Item item : items) {
-			System.out.println(item.item_name + ": " + item.value / total_score);
-		}
-			
+		/*
+		for (Item item : items) {
+			System.out.println(item.item_name + ": " + item.value);
+		} */
+
+		return items;
 	}
 
 	public void run() throws IOException {
+		List<List<String>> faults = new ArrayList<List<String>>();
+		faults.add(Arrays.asList("link2-8", "link4-9", "link5-10", "link0-5"));
+		faults.add(Arrays.asList("link3-7", "link5-11", "link0-5", "link4-10"));
+		faults.add(Arrays.asList("link2-8", "link1-2", "link0-3", "link4-10"));
+		faults.add(Arrays.asList("link0-3", "link0-2", "link1-5", "link4-9"));
+		faults.add(Arrays.asList("link2-8", "link0-2", "link0-3", "link3-6"));
+		int k = 4;
+		//////////////////////////////////////////
+		List<Double> precisions = new ArrayList<Double>();
+		List<Integer> mrrs = new ArrayList<Integer>();
+		List<Double> ds = new ArrayList<Double>();
+		
+		for (int i = 1; i <= 5; i++) {
+			AzureLocator al = new AzureLocator("z://LinkCrashDump//ping-" + k + "-" + i + "//");
+			al.getAllPath(); // get all possible shortest paths from i to j
[…]

### 2016-07-02 src/util/Util.java

@@ -8,6 +8,23 @@ import java.util.*;
 import java.util.*;
 
 public class Util {
+	public static double inverseSum(List<Integer> nums) {
+		double ret = 0;
+		for(int num : nums) {
+			ret += 1 / (double)num;
+		}
+		
+		return ret / nums.size();
+	}
+	
+	public static double average(List<Double> nums) {
+		double res = 0;
+		for(double num : nums) {
+			res += num;
+		}
+		
+		return res /= nums.size(); 
+	}
 	
 	public static void normalize(List<Item> list) {
 		double total = 0;
@@ -194,16 +211,43 @@ public class Util {
 	}
 
 	public static void main(String args[]) {
-		double p = 0.001;
+		double a[] = new double[]{0.208877,
+				0.23625,
+				0.235987,
+				0.234116,
+				0.226187,
+				0.222623,
+				0.176447,
+				0.239669,
+				0.213614,
+				0.26604,
+				0.263351,
+				0.223458,
+				0.273424
+
+
+		};
 		
-		for(int k=2; k<=6; k++) {
-			int m = 1 + k - (k+1) / 2;
-			double pro = 0;
-			for(; m<=k; m++) {
-				pro += Util.C_N_M(k, m) * Math.pow(p, m) * Math.pow(1-p, k-m);
-			}
-			System.out.println("k = " + k + ": " + pro);
+		double b[] = new double[]{0.108977,
+				0.23629,
+				0.256057,
+				0.240432,
+				0.215982,
+				0.2469,
+				0.236427,
+				0.195673,
+				0.220823,
+				0.231803,
+				0.262053,
+				0.219117,
+				0.254761
+		};
+		
+		double res = 0;
+		for(int i=0; i<a.length; i++) {
+			res += ((a[i] - b[i]) / b[i]);
 		}
-		System.out.println();
+		
+		System.out.println(res / a.length);
 	}
 }

### 2016-07-02 plot.py
plot scipt

@@ -1,0 +1,212 @@
+import matplotlib.pyplot as plt
+import numpy as np
+from pylab import *
+
+colors = ['k', 'w', 'r', 'c', 'b', 'm', 'g', 'y']
+types = ['-', '/', '|', '\\', '.', '+', '*']
+
+
+def readData(path):
+    data = []
+    file = open(path, 'r')
+
+    for line in file.readlines():
+        data.append(float(line))
+    return data
+
+
+# no crashes, having message loss
+def draw_query(names):
+    loss_rate = readData('z://plotData//crashes.txt')
+    baseline = readData('z://plotData//baseline-c-q.txt')
+    datak2 = readData('z://plotData//k2-c-q.txt')
+    datak3 = readData('z://plotData//k3-c-q.txt')
+    datak5 = readData('z://plotData//k5-c-q.txt')
+
+    p1, = plt.plot(loss_rate, baseline, 'k.-', linewidth=0.8)  # baseline
+    p2, = plt.plot(loss_rate, datak2, 'b.--', linewidth=0.8)  # k=2
+    p3, = plt.plot(loss_rate, datak3, 'r.-.', linewidth=0.8)  # k=3
+    p4, = plt.plot(loss_rate, datak5, 'g.:', linewidth=0.8)  # k=5
+
+    plt.xlabel('Number of Crash Servers', fontsize=7)  # make axis labels
+    plt.ylabel('Query Accuracy Probability', fontsize=7)
+
+    # plt.xlim(0, 0.05)
+    # plt.ylim(0.1, 1)
+
+    leg = plt.legend((p1, p2, p3, p4), (names[0], names[1], names[2], names[3]), loc='upper left', prop={'size': 5})
+    leg.draggable(state=True)
+
+    plt.tick_params(axis='x', labelsize=5)
+    plt.tick_params(axis='y', labelsize=5)
+    plt.show()
+
+
+def draw_rate(names):
+    loss_rate = readData('z://plotData//crashes.txt')
+    baseline = readData('z://plotData//baseline-c-r.txt')
+    datak2 = readData('z://plotData//k2-c-r.txt')
+    datak3 = readData('z://plotData//k3-c-r.txt')
+    datak5 = readData('z://plotData//k5-c-r.txt')
+
+    p1, = plt.plot(loss_rate, baseline, 'k.-', linewidth=0.8)  # baseline
[…]

### 2016-07-03 SIG Proceedings Template-Jan2015 Zip/paper.tex
writing Introduction part

@@
 \section{Introduction}
-Data center.
+Data center is a pool of resources interconnected using a communication network, a broad range of services (e.g., Web search, data analytic, storage backup) are hosted on data centers.
+Data center networks play a pivotal role in data centers as they integrate various resources and connect hundreds of thousands devices together (e.g.
+routers, switches, servers).
+Due to the scale of data center networks, failures are common and hence automated failure detection can help reduce mean-time-to-recovery and service disruption.
+
+However, failure detection in data center networks should not be simplex.
+On one hand, data center networks are reliable \cite{gill2011understanding} due to the built-in redundancy of data center networks like hardware redundancy and fault-tolerant routing protocols.
+For about 80\% of the links and about 60\% of the devices, there is a more than four 9's of availability.
+On the other hand, many applications hosted on data centers have very strict timing constraints \cite{tomsic20152w}, they require failure detectors to provide quality of service (QoS) with quantitative timeliness guarantees.
+
+Unfortunately, few researches have noticed QoS difference in failure detection in data center networks.
+Some researches on failure detection architecture such as \cite{felber1999failure} \cite{van1998gossip} \cite{gillen2007scalable} \cite{xu2012smart} \cite{xu2012smart} focus on scalable node or process failure detection in large scale distributed systems without considering underlying network topologies.
+Other failure detection approaches \cite{bahl2007towards} \cite{herodotou2014scalable} \cite{kandula2005shrink} treat all the network devices equally.
+
+Having realized the limitations of existing work and also to address this issue, we firstly divide network devices into two categories: imperative devices and non-imperative devices.
+including servers, top of rack switches and links between them
+
+This paper makes the following contributions:
+\begin{itemize}
+  \item To the best of our knowledge, 
+  \item 
+  \item 
+\end{itemize}
 
@@
 Section 4 provides an overview of our approach, while the details are described in Section 5.
-The experimental evaluation along with experiments results is presented in Section 6.
+The experimental evaluation along with experimental results is presented in Section 6.
 Finally, Section 7 concludes this paper.
@@
     \begin{array}{lcl}
-    \text{suspect} & \text{if} & |\left\{s|s\in ToR\right\} \cap \left\{s|S_{s,t}=\text{suspect}\right\}| \\
-    && \geq \alpha \cdot m\\
+    \text{suspect} & \text{if} & | \{s | s \in ToR, \\
+    && CRMO_{s,t} \not = \emptyset, \\
+    && |CRM_{s,t}|=1\} | \geq \alpha \cdot m \\
+
     \text{trust} && \text{otherwise}
@@
 where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion is to determine failure of a ToR.
+$CRMO_{s,t}$ denotes the collection of crash report messages of $s$ coming from outside racks until time $t$.
 When \textbf{Crash Decider} gets more than $\alpha \cdot m$ crash report messages of servers under the ToR crash, it will report the crash of ToR.
@@
 
+\subsubsection*{Upper Bound of $\alpha$}
+Theoretically, a smaller $\alpha$ means a more aggressive detection.
+We can set an appropriate $\alpha$ empirically by looking back on historical data on ToR crashes.
+Suppose we have known the ToR crash probability $p$, there are $n$ racks (each one has a ToR) and crashes of ToRs are subject to \textit{binomial distribution}:
+\begin{equation}
+    \begin{aligned}
+        &m_0  = \frac{m}{n-1}(n-k_0) = \frac{m(n-k_0)}{n-1}\\
+        &\alpha \leq \alpha_0  = \frac{m_0}{m} = \frac{n-k_0}{n-1}\\
+        &\text{where } k_0 \text{ is the minimum of } k\\
+        & s.t. \quad Pr(x\leq k) = \sum_{r=0}^k C_n^r p^r(1-p)^{n-r} \geq p_0 \\
+    \end{aligned}
+\end{equation}
+$Pr(x\leq k)$ denotes the probability of number of ToR crashes is no more than $k$, $m_0$ is the number of observed crash report messages, it equals to number of alive ToRs times number of detectors per rack.
+Consequently, given $p$ and $p_0$, the theoretical upper bound of $\alpha$ should be $\alpha_0$.
+
 To sum up, Algorithm 1 illustrates the pseudo-code for overall detection algorithm of \textbf{Crash Decider}.
-
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
@@
 \section{Evaluation}
-In this section, we will present how we evaluate our approach in terms of efficiency and effectiveness. Experiments results will also be shown in this section.
+In this section, we will present how we evaluate our approach in terms of efficiency and effectiveness. Experimental results will also be shown in this section.
 
@@
 
-\subsubsection*{RQ2: Can K-detectors model benefit ToR crash detection?}
-\quad The evaluation of failure detection for ToRs is almost the same as servers. We will evaluate the impact of different values of $\alpha$.
+\subsubsection*{RQ2: Can K-detectors model benefit ToR failure detection?}
+\quad The evaluation of failure detection for ToRs is similar to servers.
+We will evaluate the impact of different number of server crashes, that is to say, we want to see whether server failures affect the QoS of ToR failure detection.
+The evaluation metrics are the same as servers.
 
@@
 
-\subsection{Experiments Results}
+\subsection{Experimental Results}
 
@@
 \subsubsection*{RQ2: ToR crash Detection}
-\quad To answer this question,
+\quad To answer this question, we compute the metrics of ToRs failure detection in the presence of different server crashes.
+On top of this, we randomly make three ToR failure events with failure group size equals to 1, 2 and 3 respectively.
+In particular, $\alpha$ is set to 0.9, 0.6 and 0.4 when failure group size is 1, 2 and 3 respectively.
 
-The drawback of our approach is that once occurring ToR failures, we cannot detect server crashes within the rack before the ToR recovering.
+The $P_A$ and $AD_T$ are shown in Figure 8.
+Roughly speaking, size of server crashes has little impact on QoS of ToR failure detection.
+With the increasing of ToR crashes number, $AD_T$ is better due to a smaller $\alpha$, which means \textbf{Crash Decider} needs fewer crash report messages to determine the failure of a ToR.
 
-\subsubsection*{RQ3: QoS of BPNN Based Model?}
+\begin{figure}
+  \centering
+  \begin{tabular}{c}
+  \includegraphics[scale=0.7]{tor-r1} \\
+  \includegraphics[scale=0.7]{tor-r2} \\
+  \end{tabular}
+  \caption{Effect of Server Crashes on $P_A$ and $AT_D$ of ToRs}
+\end{figure}
+
+The main drawback of our approach is that once occurring ToR failures, we cannot detect server crashes within the rack before the ToR recovers.
+
+\subsubsection*{RQ3: QoS of BPNN Based Model}
 \quad To answer this question, we wants to firstly explain why we select BPNN rather other popular classifiers.
@@
 It mainly stems from the fact that our approach is based on a multi-layer perceptron architecture, it can precisely capture the characteristic of each link failure.
-But one of the drawbacks of our approach is that it requires much data and time to train BPNN offline to ensure its generalization ability, it cannot adapt to network topology changes as well.
+But one of the drawbacks of our approach is that it requires much data and time to train BPNN offline to ensure its generalization ability, it cannot adapt to network topology changes either.
 

### 2016-07-03 src/core/ServerFailureDetector.java

@@ -143,7 +143,7 @@ public class ServerFailureDetector {
 	}
 
 	public Map<Integer, List<TimePeriod>> detectToRCrash(Map<Integer, List<TimePeriod>> alerts) {
-		final double alpha = 0.9;
+		final double alpha = 0.4;
 		
 		Map<Integer, List<TimePeriod>> tor_alerts = new HashMap<Integer, List<TimePeriod>>();
 		
@@ -218,14 +218,18 @@ public class ServerFailureDetector {
 		}
 	}
 	
+	// run for ToR detection
 	public void run1() throws IOException {
-		for(int i = 1; i <= 1; i++) {
+		final int num_tor_crash = 3;
+		int server_crash[] = new int[]{0};
+		
+		for(int i : server_crash) {
 			ServerFailureDetector sfd = new ServerFailureDetector(
-					"z://torCrashDump//tor-1-" + i +"//", 
+					"z://torCrashDump//tor-" + num_tor_crash + "-" + i +"//", 
 					false, 
-					"z://crashFile//server-crash-1.txt",
+					"z://crashFile//server-crash-" + i +".txt",
 					true,
-					"z://crashFile//tor-crash-1-" + i + ".txt");
+					"z://crashFile//tor-crash-" + num_tor_crash + ".txt");
 			
 			Map<Integer, List<TimePeriod>> alerts = sfd.detect(3, true, 0.001);	
 			
@@ -236,26 +240,27 @@ public class ServerFailureDetector {
 			}*/
 			
 			Map<Integer, List<TimePeriod>> tor_alerts = sfd.detectToRCrash(sfd.raw_reports);
-			
+			/*
 			for(Map.Entry<Integer, List<TimePeriod>> entry : tor_alerts.entrySet()) {
 				if(entry.getValue().size() > 0)
 					System.out.println(entry.getKey() + "  " + entry.getValue());
-			}
+			}*/
 			
+			System.out.println("# server crash: " + i + "# tor crash " + num_tor_crash);
 			System.out.println("average detection time: " + Evaluator.avgDetectionTime(tor_alerts, sfd.tor_crashes));
 			System.out.println("mistake rate: " + Evaluator.faultCrashReportRate4ToR(tor_alerts, sfd.tor_crashes));
 			System.out.println("average query accuracy: " + Evaluator.avgQueryAccuracyPro4ToR(tor_alerts, sfd.tor_crashes));
-
+			System.out.println();
 		}
[…]

### 2016-07-03 src/evaluation/Evaluator.java

@@ -18,11 +18,14 @@ public class Evaluator {
 			double real_time = entry.getValue();
 			
 			double suspect_time = -1;
-			for(TimePeriod tp : alerts.get(crash_id)) {
-				if(tp.end >= real_time) {
-					suspect_time = tp.begin;
-					break;
+			if(alerts.containsKey(crash_id)) {
+				for(TimePeriod tp : alerts.get(crash_id)) {
+					if(tp.end >= real_time) {
+						suspect_time = tp.begin;
+						break;
+					}
 				}
+
 			}
 			if(suspect_time == -1) {
 				num_crash--;

### 2016-07-05 SIG Proceedings Template-Jan2015 Zip/paper.tex
experiment data && paper first draft

@@
 
-\title{A Failure Detection Approach of Data Center Networks\titlenote{(Produces the permission block, and
-copyright information). For use with
-SIG-ALTERNATE.CLS. Supported by ACM.}}
+\title{A Novel Failure Detection Solution with Multiple QoS in Data Center Networks }
 %
@@
 \alignauthor
-Kai Shen\titlenote{Dr.~Trovato insisted his name be first.}\\
+Kai Shen\\
        \affaddr{School of Software}\\
@@
 \alignauthor
-????\titlenote{Dr.~Trovato insisted his name be first.}\\
-       \affaddr{School of Software}\\
+????\\
+       \affaddr{????}\\
        \affaddr{Shanghai Jiao Tong University}\\
@@
 }
-% There's nothing stopping you putting the seventh, eighth, etc.
-% author on the opening page (as the 'third row') but we ask,
-% for aesthetic reasons that you place these 'additional authors'
-% in the \additional authors block, viz.
-% Just remember to make sure that the TOTAL number of authors
-% is the number that will appear on the first page PLUS the
-% number that will appear in the \additionalauthors section.
+
 \maketitle
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
+Large scale data center networks are complex due to hundreds of thousands devices and links in them.
+Failures of these devices and links sometimes can lead to user-perceived service interruptions.
+Thus automated failure detection plays a very important role in maintaining the reliability of data centers.
+Many researches have been performed on failure detection in networks or distributed systems, but few of them identifies quality of service (QoS) multiplicity of failure detection in data center networks.
 
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
+In this paper, to tackle with this problem, we firstly divide network devices into two categories: imperative devices whose failures need to be detected in real time, and non-imperative devices.
+Subsequently, we leverage a co-detection approach named K-detectors to detect failures of imperative devices, while the key idea of non-imperative devices failure detection is to analyze network traffic changes over time.
 
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
+We evaluate our approach on a simulated network built by ns-3.
+Experimental results show that for imperative devices, our approach has a better QoS except for limited detection time increase in the presence of normal message loss and different size of failures.
+For non-imperative devices, our approach outperform existing work in terms of accuracy and failure discrimination.
 \end{abstract}
@@
 %
-\printccsdesc
+%\printccsdesc
 
@@
 routers, switches, servers).
-Due to the scale of data center networks, failures are common and hence automated failure detection can help reduce mean-time-to-recovery and service disruption.
+For example, the Microsoft Live online services are supported by a Chicago-based
+data center spanning more than 700,000 square feet \cite{DBLP:series/sbcs/LiuMVLH13}.
+
+Due to the complexity and scale of data center networks, failures are common.
+Hence it is crucial to detect failures in the networks efficiently and effectively.
+Traditionally, domain experts are responsible for failure detection with the help of network monitoring data.
+But such a manual process is time-consuming, error-prone and not scalable.
+So automated failure detection approaches are useful in terms of helping reduce mean-time-to-recovery and service disruption.
 
 However, failure detection in data center networks should not be simplex.
-On one hand, data center networks are reliable \cite{gill2011understanding} due to the built-in redundancy of data center networks like hardware redundancy and fault-tolerant routing protocols.
-For about 80\% of the links and about 60\% of the devices, there is a more than four 9's of availability.
+On one hand, data center networks are reliable due to the built-in redundancy of data center networks like hardware redundancy and fault-tolerant routing protocols.
+Evidence shows that for about 80\% of the links and about 60\% of the devices, there is a more than four 9's of availability \cite{gill2011understanding}.
 On the other hand, many applications hosted on data centers have very strict timing constraints \cite{tomsic20152w}, they require failure detectors to provide quality of service (QoS) with quantitative timeliness guarantees.
 
-Unfortunately, few researches have noticed QoS difference in failure detection in data center networks.
-Some researches on failure detection architecture such as \cite{felber1999failure} \cite{van1998gossip} \cite{gillen2007scalable} \cite{xu2012smart} \cite{xu2012smart} focus on scalable node or process failure detection in large scale distributed systems without considering underlying network topologies.
-Other failure detection approaches \cite{bahl2007towards} \cite{herodotou2014scalable} \cite{kandula2005shrink} treat all the network devices equally.
+Unfortunately, few researches have noticed QoS difference in failure detection of data center networks.
+Some researches on failure detection architecture such as \cite{felber1999failure}\cite{van1998gossip}\cite{gillen2007scalable}\cite{xu2012smart}\cite{xu2012smart} focus on the scalability issue of process crash detection in large scale distributed systems without considering underlying network topologies, while other work on failure localization in data center networks such as \cite{bahl2007towards}\cite{herodotou2014scalable}\cite{kandula2005shrink} treat all the network devices equally and utilize a general detection approach.
 
-Having realized the limitations of existing work and also to address this issue, we firstly divide network devices into two categories: imperative devices and non-imperative devices.
-including servers, top of rack switches and links between them
+To address this issue, we firstly divide network devices into two categories: imperative devices and non-imperative devices.
+Imperative devices mainly include servers, top of rack switches and links between them, while non-imperative devices include other routers, switches and links.
+The main difference between them is that imperative devices have strict timing constraints of QoS as the failures of them may affect application functionalities.
+Naturally, our detection approach is two-fold: for imperative devices, we propose a co-detection model called K-detectors model to ensure the timeliness, soundness and accuracy at the same time.
+For non-imperative devices, we utilize a data mining based model to produce a ranked list consisting of suspect devices by extracting network traffic features.
+To evaluate our work, we compare our approach with hierarchical detection architecture \cite{felber1999failure} in terms of detection for imperative devices, and the work of Herodotou et al.
+\cite{herodotou2014scalable} in terms of detection for non-imperative devices.
+The experimental results prove the effectiveness of our work.
 
@@
 \begin{itemize}
-  \item To the best of our knowledge, 
-  \item 
-  \item 
+  \item We identify the differences in QoS of failure detection in data center networks.
+  \item We further divide network devices into two categories and propose effective failure detection approaches for these two kinds of devices respectively.
+  \item We set up a series of evaluation metrics to evaluate different aspects of failure detection approaches.
+  \item We implement our approach as well as other baselines on the same simulated data center network and prove the effectiveness of our approach.
 \end{itemize}
@@
 \section{Related Work}
-In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure detection in data center networks.
+In this section, we will present various relevant works including failure detectors, failure detection architecture in distributed systems and failure detection in networks.
 
@@
 proposed a FD that provides QoS \cite{chen2002quality}.
-It estimates the expected arrival time (EAs) of the next heartbeat message according to a slide window storing n most recent arrived messages.
+It estimates the expected arrival time (EAs) of the next heartbeat message according to a slide window storing $n$ most recent arrived messages.
 EAs determine the deadline that the detector will wait for the next heartbeat before suspecting the monitored process.
@@
 proposed a similar FD \cite{bertier2002implementation}, whereas it uses a dynamic way to compute error margin of \textit{Chen FD}.
-Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output a continuous accrual failure value other than a binary value at any time which stands for the failure probability of the process.
+Other FDs like \textit{$\phi$ Accrual FD} \cite{hayashibara2004varphi} and \textit{Satzger FD} \cite{satzger2007new} can output a continuous accrual failure value rather than a binary value which stands for the failure probability of the process at any time.
 
@@
 The first one is hierarchical architecture \cite{felber1999failure}, all the nodes are partitioned into different groups, each group has a leader node.
-Within a group, the leader node is responsible for monitoring all the nodes.
+Within a group, the leader node is responsible for monitoring all the other nodes.
 Leader nodes periodically send node status information of his group to other leader nodes.
@@
 \subsection{Failure Detection in Networks}
-Different from the work mentioned above, failure detection in networks should consider network topology and localize failure positions at IP layer.
+Different from the work mentioned above, failure detection in networks take network topology into consideration and localize failure positions at IP layer.
 Gill et al.
@@
 Also, there exists a large body of work on applying statistical approaches to failure localization in networks.
-Sherlock \cite{bahl2007towards} localizes failures to limited network components by capturing dependencies between components.
-Shrink \cite{kandula2005shrink} leverages Bayesian Network model to diagnose root cause of IP network failures.
+\textit{Sherlock} \cite{bahl2007towards} localizes failures to limited network components by capturing dependencies between components.
+\textit{Shrink} \cite{kandula2005shrink} leverages Bayesian Network model to diagnose root cause of IP network failures.
 Herodotou et al.
-\cite{herodotou2014scalable} actively inject ping traffic into network and analyze the ping results overlaid on top of the network topology.
-It will generate a ranked list containing the suspected failed device and links along with their failure score that can best explain the observed ping data.
+\cite{herodotou2014scalable} actively inject ping traffic into network and analyze the ping results overlaid on top of the network topology, it generates a ranked list containing the suspected failed device and links along with their failure score that can best explain the observed ping data.
+
+% figure
+\begin{figure}[t]
+\centering
+\includegraphics{topology}
+\caption{Conventional Data Center Network Topology}
+\end{figure}
 
@@
 A data center is a facility used to house computer systems and associated components, it usually contains hundreds of thousands devices and links.
-Modern data centers use hierarchical architecture.
-Figure 1 depicts a conventional data center network architecture \cite{gill2011understanding, greenberg2009vl2, herodotou2014scalable}.
+Modern data centers use hierarchical architectures.
+Figure 1 depicts a conventional data center network architecture \cite{gill2011understanding}\cite{greenberg2009vl2}\cite{herodotou2014scalable}.
 At the bottom layer are racks of servers, typically there are 20 to 40 servers in each rack, and each server in the same rack connects to a Top of Rack (ToR) Switch via a 1 Gbps link.
@@
 Finally, ARs are connected to Core Routers (CRs).
+CRs are at the boundary of a data center network.
 
-To limit overheads and to isolate different services, servers are partitioned into virtual LANs (VLANs).
+To limit overheads and also to isolate different services, servers are partitioned into virtual LANs (VLANs).
 All links in the data center use Ethernet as link layer protocol and physical connections are a mix of copper and fiber cables.
-In addition to the devices in Figure 1, there may exist other devices like load balancers (LBs) and firewalls.
+In addition to the devices in Figure 1, there may exist other devices like Load Balancers (LBs) and Firewalls.
 
-Modern data center usually employs \textit{Equal Cost MultiPath} (ECMP) routing within the data center for fault tolerance, which means that there are multiple paths from source to destination.
+Modern data center usually employs \textit{Equal Cost MultiPath (ECMP)} routing within the data center for fault tolerance, which means that given a source and destination, there are multiple paths from the source to the destination.
 Thus in this work, we will apply ECMP routing to the simulated network by enabling ECMP routing configurations in ns-3.
-
-% figure
-\begin{figure}
-\centering
-\includegraphics{topology}
-\caption{Conventional Data Center Network Topology}
-\end{figure}
 
@@
 
-Different network device should have different quality of service (QoS).
+As we mentioned in Section 1, different network device should have different quality of service (QoS).
 Gill et al.
@@
 declare that the downtime of ToRs may be very long.
-Thus the failure detection for these devices must be fast enough besides the accuracy requirement.
+Thus the failure detection for these devices must be fast enough besides other requirements.
 
 \item \textbf{Non-imperative Device.} It includes links, other routers and switches.
-A single failure of a link or a router does not affect the functionality of a data center because of path redundancy.
-So administrators care more about how effective the detect service is (The ability to identify actually happening failures).
+A single failure of a link or a router does not affect the functionality of a data center because of built-in redundancy in data centers.
+So the data center administrators care more about whether the detection service is accurate enough to help them localize the real faults.
 
@@
 % figure
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 It mainly contains two modules.
-The servers failure detection system combines centralized with decentralized structures.
+The upper half part illustrates the module for server failure detection.
+It is a combination of centralized and decentralized structures.
 A server can both play the role of a detector and a monitored object.
 Each server is monitored by multiple FD processes installed on different servers for redundancy.
-A server can also monitor a couple of servers.
-Once the FD outputs the crash of a server, it will send a crash report message to \textbf{Crash Decider}.
+A server can also monitor a group of servers.
+Once a FD determines the crash of a server, it will send a crash report message to \textbf{Crash Decider}.
 \textbf{Crash Decider} will determine the final status of this server.
+On top of this, \textbf{Crash Decider} is also responsible for detecting ToR failures by combining all the server crash report messages together.
 
@@
 \section{Failure Detection Approach}
-In this section, we will discuss the detailed design of different modules of the failure detection system respectively.
+In this section, we will discuss the detailed design of different aspects of the failure detection system respectively.
 
 \subsection{K-detectors Model}
-To detect the crash of servers and ToRs effectively and efficiently, this paper propose a detection model named $K$-detectors model.
+To detect the crash of servers and ToRs effectively and efficiently, this paper propose a co-detection model named $K$-detectors model.
 Our detection model is based on the assumption that once the server or ToR crashes, it never recovers by itself.
-The QoS of failure detection are as follows:
+We first refine the QoS of failure detection for servers:
 
 \begin{itemize}
-\item \textbf{Efficiency.} It measures how fast the system can report the crash after it crashes. The system is more efficient if it takes less time to detect a failure.
+\item \textbf{Efficiency.} It measures how fast the system can report the crash after it crashes.
+The system is more efficient if it takes less time to detect a failure.
+In particular, server failures should be detected in real time.
 \item \textbf{Completeness.} It measures whether the system can detect all the crashed objects. The system is more complete if it rules out fewer true crashed ones.
@@
 For example, message loss and message delay may happen sometimes.
-The detection system should be sound enough to distinguish between such condition and a real crash.
+The detection system should be sound enough to distinguish between such conditions and a real crash.
 
@@
 
-In $K$-detectors model, each server is monitored by $K$ FDs on different servers where $K$ is a parameter tuned by users.
+In $K$-detectors model, each server is monitored by $K$ FDs on different servers where $K$ is a parameter tuned by user applications.
 When a FD considers a server crashes, it sends a crash report message to \textbf{Crash Decider}.
@@
     \begin{array}{lcl}
-    \text{suspect} & \text{if} & |CRM_{s,t}|\geq\left\lfloor(K+1)/2\right\rfloor \\
+    \text{suspect} & \text{if} & |\,CRM_{s,t}\,|\geq\left\lfloor(K+1)/2\right\rfloor \\
 
@@
 If \textbf{Crash Decider} receives $\left\lfloor(K+1)/2\right\rfloor$ crash messages of a server, it considers the server to have crashed.
+So a server is still under monitor even when a number of its FDs crash.
 
 \subsection{Monitoring Rule Inference}
-To form the $K$-detectors model and also to meet QoS to the greatest extent, we propose the following specifications of monitoring relationships among servers:
+A monitoring rule defines the monitoring relationships among a group of servers.
+To form the $K$-detectors model and also to meet QoS to the greatest extent, we propose the following specifications of a monitoring rule:
 \begin{enumerate}
@@
 Also, $K$-detectors can prevent crashes of FDs to some extent.
-Theoretically, a failure can still be detected even when $K-\left\lfloor(K+1)/2\right\rfloor=\left\lfloor K/2\right\rfloor$ of its detectors crashed.
+Theoretically, a failure can still be detected even when $K-\left\lfloor(K+1)/2\right\rfloor=\left\lfloor K/2\right\rfloor$ of its detectors crash.
 
@@
 
-The last one is an extension of specification five. It is for the consideration of ToRs' detection, we will discuss it in detail in Section 5.4.
+The last one is an extension of specification five. It is for the consideration of ToRs' failure detection, we will discuss it in detail in Section 5.4.
 
 \subsection{FD Algorithm}
-FD algorithm is used to decide the status of one monitored object by one FD. Our FD algorithm is almost the same as \textit{Chen} FD \cite{chen2002quality} except for some minor changes.
+FD algorithm is used to decide the status of one monitored object by one FD. Our FD algorithm is almost the same as \textit{Chen FD} \cite{chen2002quality} except for some minor changes.
 
@@
 
-After that, we utilize hyperbolic tangent function to model current suspicious level:
+After that, we utilize Hyperbolic Tangent Function to model current suspicious level:
 
 \begin{equation}
-\tau(t_{now}) = |tanh(t_{now}-EA_{l+1})|
+\tau(t_{now}) = |\,tanh(t_{now}-EA_{l+1})\,|
 \end{equation}
-suspicious level $\tau(t_{now})$ always ranges from 0 to 1, when $t_{now}$ grows bigger, the suspicious level is closer to 1, which implies a higher failure probability.
+Hyperbolic Tangent Function is one of the widely used activation functions in neural networks.
+The suspicious level $\tau(t_{now})$ always ranges from 0 to 1, when $t_{now}$ grows bigger, the suspicious level is closer to 1, which implies a higher failure probability.
 A continuous valued rather than binary valued output decouples the interpretation of failure data from the failure monitoring mechanism, user applications can set their own threshold according to their demands.
@@
 Apart from determination of servers' crashes, \textbf{Crash Decider} is also responsible for failure detection for ToRs.
-If most or even all servers in a rack is reported crash by FDs of other racks, it is more likely that the top of rack switch crashes rather than the servers.
+The essential idea is that if most or even all servers in a rack is reported crash by FDs in other racks, it is more likely that the top of rack switch crashes rather than the servers.
 
@@
     \begin{array}{lcl}
-    \text{suspect} & \text{if} & | \{s | s \in ToR, \\
+    \text{suspect} & \text{if} & |\, \{s\, |\, s \in ToR, \\
     && CRMO_{s,t} \not = \emptyset, \\
-    && |CRM_{s,t}|=1\} | \geq \alpha \cdot m \\
+    && |\,CRM_{s,t}\,|=1\} \,| \geq \alpha \cdot m \\
 
@@
 The last specification in Section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure.
+Suppose there are $n$ racks in total, according to this specification, for each rack $r$, each other rack will monitor $m/(n-1)$ servers of rack $r$.
 An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.
@@
 We can set an appropriate $\alpha$ empirically by looking back on historical data on ToR crashes.
-Suppose we have known the ToR crash probability $p$, there are $n$ racks (each one has a ToR) and crashes of ToRs are subject to \textit{binomial distribution}:
+Suppose we have known the ToR crash probability $p$, there are $n$ racks (each one has a ToR) and crashes of ToRs are subject to \textit{binomial distribution}.
+When there are $k$ ToR crashes, the number of server crash report messages we can observe $m^\prime$ should be
+\begin{equation}
+    m^\prime  = \frac{m}{n-1}(n-k) = \frac{m(n-k)}{n-1}
+\end{equation}
+Thus the value of $\alpha$ is at most:
+\begin{equation}
+    \alpha  = \frac{m^\prime}{m} = \frac{n-k}{n-1}
+\end{equation}
+Next, if given a confidence parameter $p_0$,
 \begin{equation}
     \begin{aligned}
-        &m_0  = \frac{m}{n-1}(n-k_0) = \frac{m(n-k_0)}{n-1}\\
-        &\alpha \leq \alpha_0  = \frac{m_0}{m} = \frac{n-k_0}{n-1}\\
+        &\alpha \leq \alpha_0  = \frac{m_0^\prime}{m} = \frac{n-k_0}{n-1}\\
         &\text{where } k_0 \text{ is the minimum of } k\\
@@
 \end{equation}
-$Pr(x\leq k)$ denotes the probability of number of ToR crashes is no more than $k$, $m_0$ is the number of observed crash report messages, it equals to number of alive ToRs times number of detectors per rack.
-Consequently, given $p$ and $p_0$, the theoretical upper bound of $\alpha$ should be $\alpha_0$.
+$Pr(x\leq k)$ denotes the probability of number of ToR crashes is no more than $k$.
+Hence the theoretical upper bound of $\alpha$ is $\alpha_0$.
+Actually, because of server crashes, the number of crash report messages \textbf{Crash Decider} can receive may less than observe $m_0^\prime$, so the value of $\alpha$ should be less than its upper bound.
 
@@
 		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
-		\ENSURE $S_{i,t}$, $i$ is an imperative device
+		\ENSURE $S_{i,t}$, $i \in \text{Imperative Device}$
 
-        \FOR{$i \text{ in imperative devices}$}
+        \FOR{$i \text{ in Imperative Devices}$}
             \STATE $S_{i,t_0} \leftarrow trust$
@@
                 \STATE $rackID \leftarrow getRackID(i)$
-                \IF{$|CRM_{i,t_{now}}| \geq \left\lfloor(K+1)/2\right\rfloor$}
+                \IF{$|\,CRM_{i,t_{now}}\,| \geq \left\lfloor(K+1)/2\right\rfloor$}
                     \STATE $S_{i,t_{now}} \leftarrow suspect$
@@
 
-            \FOR{each i in ToRs}
+            \FOR{$\text{each } i \text{ in ToRs}$}
                 \IF{$failsEachRack.get(i) \geq \alpha \cdot m$}
@@
 It firstly determines the status of each server (line 6 to 16), and then determines the status of ToRs (line 17 to 23).
-When detecting server failures, \textbf{Crash Decider} also records necessary information to find potential ToR crashes (line 12 to 13).
+When detecting server failures, \textbf{Crash Decider} also records necessary information to find potential ToR crashes (line 12 to 14).
 
 \subsection{Failure Detection for Links}
-The failure detection for links is another important part of our detection system, this paper presents the following QoS:
+The failure detection for non-imperative devices is another important part of our detection system.
+Failures of routers and switches can be easily detected by checking traffic dump on them.
+So in this subsection, we will focus on detection for links.
+We firstly refine the following QoS:
 \begin{itemize}
@@
 The insight is that network traffic distribution is associated with routing protocol and monitoring relationships of servers, the drastic changes of traffic probably imply failures.
-For example, if the network topology is just as Figure 1 shows, when the link between the leftmost AR and the leftmost AS fails, the traffic on the leftmost AR will decrease and the rightmost AR's traffic will increase according to ECMP routing.
+For example, if the network topology is just as Figure 1 shows, when the link between the leftmost AR and the leftmost AS fails, the heartbeat traffic on the leftmost AR will decrease and the rightmost AR's heartbeat traffic will increase according to \textit{ECMP} routing.
 
@@
 As is shown in Figure 3, BPNN is a multi-layer perceptron architecture:
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
         \FOR{\unboldmath $i \in E$}
-            \STATE $F_i \leftarrow \frac{\Delta T F_i}{t}$
+            \STATE $F_i \leftarrow \frac{\Delta T \cdot F_i}{t}$
         \ENDFOR
@@
 Algorithm 2 shows the algorithm of \textbf{Traffic Analysis Worker}.
-The input of the algorithm is the refined time series traffic data over time $T$.
+The input of the algorithm is the refined time series traffic data over time $t$.
 Firstly, traffic data is divided into chunks.
-Each chunk represents a time unit $\Delta T$ (line 1) of traffic.
+Each chunk represents a time unit $\Delta T$ of traffic (line 1).
 The last chunk will be dropped if its time period is less than $\Delta T$.
@@
 For example, when there are only one faulty links in the network, the failure score of the sole faulty link will be very high, which in turn makes its final failure score higher.
-However, it does not matter because we care more about whether it can find as many failures rather than the ranking.
+However, it does not matter because we care more about whether it can find more failures rather than the ranking.
 
 \section{Evaluation}
-In this section, we will present how we evaluate our approach in terms of efficiency and effectiveness. Experimental results will also be shown in this section.
+In this section, we will present how we evaluate our approach. Experimental results will also be shown in this section.
 
@@
 ns-3 is a discrete-event network simulator for Internet systems, targeted primarily for research and educational use \cite{henderson2008network}.
-we install ns-3 on single PC with 2 cores, 3.4 GHz CPU and 4GB RAM.
+We install ns-3 on single PC with 2 cores, 3.4 GHz CPU and 4GB RAM.
 The version of ns-3 we use is ns-3.24.
@@
 \subsection{Research Questions}
-The objective of our experiments is to validate the effectiveness and efficiency of the proposed approach compared with baselines. For this purpose, we set up the following research questions:
+The objective of our experiments is to validate the effectiveness of the proposed approach compared with baselines. For this purpose, we set up the following research questions:
 
-\subsubsection*{RQ1: How about the QoS of K-detectors model?}
+\subsubsection*{RQ1: Can K-detectors model benefit server failure detection?}
 \quad RQ1 evaluates QoS of failure detection for servers. To answer this question, we firstly set four metrics \cite{chen2002quality} corresponding to the QoS in Section 5.1.
@@
 It equals the number of such mistakes per unit of time.
-Suppose Figure 4 depicts the monitoring of the object in one time unit, the mistake rate of this FD is two.
-\begin{figure}
+For example, suppose Figure 4 depicts the monitoring of the object in one time unit, the mistake rate of this FD is two.
+\begin{figure}[t]
   \centering
@@
 
-  \item \textbf{Number of Undetected Crashes} measures the number of ignored real crash servers.
+  \item \textbf{Number of Undetected Crashes} measures the number of ignored real crash servers. This metric measures the completeness of the approach.
 \end{itemize}
@@
 
-\subsubsection*{RQ3: How about the QoS of BPNN based model?}
-\quad This RQ evaluates whether the proposed approach is more effective in detecting link failures. We make another three metrics:
+\subsubsection*{RQ3: Is the BPNN based approach effective?}
+\quad This RQ evaluates whether the proposed approach is more effective in detecting link failures than existing work. We make another three metrics:
 \begin{itemize}
@@
         \end{equation}
-        where $F_i$ is a normalized failure score of link $i$. A smaller DS implies that the results of ranked list is more determinate, which makes it easier for further troubleshooting.
+        where $F_i$ is a normalized failure score of link $i$.
+We leverage this metric to evaluate discrimination of different detection approaches.
+A smaller DS implies that the results of ranked list is more determinate, which makes it easier for further troubleshooting.
 
@@
 
-\subsubsection*{RQ1: QoS of K-detectors Model}
+\subsubsection*{RQ1: Server crash detection}
 \quad We evaluate our approach in the presence of different degrees of message loss and server crashes.
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 \end{figure}
-Figure 5 depicts $P_A$ and $AR_M$ of K-detectors and hierarchical architecture under different number of message loss without server crashes.
-Both the time and channel of message loss is chosen randomly.
-When loss rate is under 1\%, 5-detectors has about an 8.2\% improvement in $P_A$ compared with hierarchical architecture.
-When loss rate is over 0.6\%, 5-detectors makes more mistakes than others, this is probably because other methods make mistakes with relatively longer time.
-In a nutshell, with a larger parameter $K$, our approach behaves better in the presence of normal message loss.
-However, it cannot maintain with the increasing number of message loss.
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 \end{figure}
+
+Figure 5 depicts $P_A$ and $AR_M$ of K-detectors and hierarchical architecture under different number of message loss without server crashes.
+Both the time and channel of message loss is chosen randomly.
+When loss rate is under 1\%, 5-detectors has about an 8.2\% improvement in $P_A$ compared with hierarchical architecture.
+When loss rate is over 0.6\%, 5-detectors makes more mistakes than others, this is probably because other methods make mistakes with relatively longer time.
+In a nutshell, with a larger parameter $K$, our approach behaves better in the presence of normal message loss.
+However, it cannot maintain with the increasing number of message loss.
+
 Subsequently, we investigate it when there exists server crashes.
@@
 \end{figure}
-
-Empirically, parameters for BPNN is set as follows: learning rate equals 0.3, number of iterations equals 500, momentum equals 0.2, number of neurons at the hidden layer is $(\# attributes + \# classes) / 2$, $\Delta T = 1 $ s.
-The selection of $\Delta T$ is a tradeoff, when $\Delta T$ grows bigger, it may contain multiple failures which violates our assumption, while a smaller $\Delta T$ may add more occasionality to traffic data.
-
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 \end{figure}
+\begin{figure}[t]
+  \centering
+  \includegraphics[scale=0.7]{ds} \\
+  \caption{DS of Different Failure Group Size}
+\end{figure}
+Empirically, parameters for BPNN is set as follows: learning rate equals 0.3, number of iterations equals 500, momentum equals 0.2, number of neurons at the hidden layer is $(\# attributes + \# classes) / 2$, $\Delta T = 1 $ s.
+The selection of $\Delta T$ is a tradeoff, when $\Delta T$ grows bigger, it may contain multiple failures which violates our assumption, while a smaller $\Delta T$ may add more occasionality to traffic data.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.7]{ds} \\
-  \caption{DS of Different Failure Group Size}
-\end{figure}
-
-Figure 8,9 and 10 show the results of out experiments.
+Figure 9, 10 and 11 show the results of out experiments.
 Our approach has a better performance in terms of percision@k and MRR.
@@
 
-On the other hand, there is a huge improvement in terms of DS.
+On the other hand, there is a huge improvement (nearly 12-folds improvement) in terms of DS.
 The approach proposed by Herodotou et al.
@@
 \section{Conclusions}
-In this paper, we described a complete failure detection approach for data center networks which leverages data mining techniques. 
-%\end{document}  % This is where a 'short' article might terminate
+Failure detection plays a very important role in maintaining the reliability of data center networks.
+In this paper, we firstly identify the differences in QoS of failure detection for different network devices.
+We leverage K-detectors model to enhance the timeliness, accuracy and soundness of failure detection for imperative devices.
+We leverage a data mining based approach to produce a ranked list of the most suspect non-imperative devices by capturing network traffic features.
+We have implemented our approach as well as baselines on a simulated data center network built by ns-3.
+Our experimental evaluation has validated the effectiveness of our approach.
 
@@
 
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
 \bibliographystyle{abbrv}
-\bibliography{paper}  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
+\bibliography{paper}
 

### 2016-07-06 plot.py
compress directories

@@ -186,6 +186,54 @@ def draw_ds(labels, data):
 
     plt.show()
 
+##########################################################
+def draw_tor_accuracy(names):
+    crashes = readData('z://plotData//#server-crash.txt')
+    data1 = readData('z://plotData//accurate-1.txt')
+    data2 = readData('z://plotData//accurate-2.txt')
+    data3 = readData('z://plotData//accurate-3.txt')
+
+    p1, = plt.plot(crashes, data1, 'k.-', linewidth=0.8)
+    p2, = plt.plot(crashes, data2, 'bo--', linewidth=0.8)
+    p3, = plt.plot(crashes, data3, 'r^-.', linewidth=0.8)
+
+    plt.xlabel('Number of Crash Servers', fontsize=7)  # make axis labels
+    plt.ylabel('Query Accuracy Probability', fontsize=7)
+
+    # plt.xlim(0, 0.05)
+    plt.ylim(0.5, 1)
+
+    leg = plt.legend((p1, p2, p3), (names[0], names[1], names[2]), loc='upper left', prop={'size': 5})
+    leg.draggable(state=True)
+
+    plt.tick_params(axis='x', labelsize=5)
+    plt.tick_params(axis='y', labelsize=5)
+    plt.show()
+
+def draw_tor_time(names):
+    crashes = readData('z://plotData//#server-crash.txt')
+    data1 = readData('z://plotData//time-1.txt')
+    data2 = readData('z://plotData//time-2.txt')
+    data3 = readData('z://plotData//time-3.txt')
+
+    p1, = plt.plot(crashes, data1, 'k.-', linewidth=0.8)
+    p2, = plt.plot(crashes, data2, 'bo--', linewidth=0.8)
+    p3, = plt.plot(crashes, data3, 'r^-.', linewidth=0.8)
+
+    plt.xlabel('Number of Crash Servers', fontsize=7)  # make axis labels
+    plt.ylabel('Average Detection Time', fontsize=7)
+
+    # plt.xlim(0, 0.05)
+    plt.ylim(0.3, 0.65)
+
+    leg = plt.legend((p1, p2, p3), (names[0], names[1], names[2]), loc='upper left', prop={'size': 5})
+    leg.draggable(state=True)
+
+    plt.tick_params(axis='x', labelsize=5)
+    plt.tick_params(axis='y', labelsize=5)
+    plt.show()
+
+
[…]
